\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{3: Due 05/26}{Mathematics is not about numbers, equations, computations, or algorithms: it is about understanding.}{William Paul Thurston}

% Problem 1
\problem{10} Suppose a course grade consists of the following weights:
	\begin{table}[!ht]
	\centering
	\begin{tabular}{rl}
	Homework & 30\% \\
	Quizzes & 15\% \\
	Exam 1 & 20\% \\
	Exam 2 & 20\% \\
	Final Exam & 10\% \\
	Project & 5\%
	\end{tabular}
	\end{table} \par
Suppose also that a student had a 86\% homework average, 90\% quiz average, 72\% on exam 1, 87\% on exam 2, 95\% on the final, and 82\% on the project. Compute the student's course average.
	



\newpage



% Problem 2
\problem{10} Suppose a GPA consists of the following weights:
	\begin{table}[!ht]
	\centering
	\begin{tabular}{lr|lr}
	A & 4.0 & C+ & 2.3 \\
	A$-$ & 3.7 & C & 2.0 \\
	B+ & 3.3 & C$-$ & 1.7 \\
	B & 3.0 & D & 1.0 \\
	B$-$ & 2.7 & F & 0.0
	\end{tabular}
	\end{table} \par
Suppose a student had the following grades on their courses:
	\begin{table}[!ht]
	\centering
	\begin{tabular}{lcl}
	Course & Credits & Grade \\ \hline
	Survey of Literature & 3 & B$-$ \\
	Freshman Seminar & 1 & A \\
	Physics I & 4 & C+ \\
	World Cultures & 3 & A$-$ \\
	Spanish I & 3 & B \\
	Algebra II & 4 & D \\
	Macroeconomics & 3 & B+
	\end{tabular}
	\end{table}
Compute this student's GPA.



\newpage



% Problem 3
\problem{10} Compute the following percentages:
	\begin{enumerate}[(a)]
	\item 40\% of 260
	\item 35\% of 1050
	\item 110\% of 37
	\item 13\% of 810
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Compute the following:
	\begin{enumerate}[(a)]
	\item 600 increased by 80\%
	\item 28 decreased by 60\%
	\item 730 increased by 170\%
	\item 45 decreased by 99\%
	\end{enumerate}



\newpage



% Problem 5
\problem{10} Convert 15~mi/min to m/s. [1~mi $=$ 520~ft; 1~m $=$ 3.28084~ft]



\newpage



% Problem 6
\problem{10} How many feet are in 1~furlong? [1~furlong $= \frac{1}{8}$~mi; 1~mi $=$ 5280~ft]



\newpage



% Problem 7
\problem{10} Convert 0.1~mi$^2$/s to ft$^2$/min. [1~mi $=$ 5280~ft]



\newpage



% Problem 8
\problem{10} Sand is filling into a giant rectangular container that is 5~ft wide, 8~ft long, and 1.5~ft deep. If the sand is flowing in at a rate of 0.6~ft$^3$/min, how long until the container is full? 



\newpage



% Problem 9
\problem{10} Suppose a horse bet pays \$19 for every \$2.50 bet. If you bet \$227 and win, how much should you expect to be paid?



\newpage



% Problem 10
\problem{10} If you use 5 bags of flour every 7~months, how many should you purchase to have enough flour to last you 3 years? If a bag of flour costs you \$4.19, how much do you spend purchasing this amount?


\end{document}