\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{16: Due 01/19}{There are two kinds of statistics: the kind you look up and the kind you make up.}{Rex Stout}

% Problem 1
\problem{10} A bag contains 15~red marbles and 15~blue marbles. Explain why the probability of drawing two red marbles in a row without replacement is \textit{not} $\dfrac{15}{30} \cdot \dfrac{15}{30}$. 



\newpage



% Problem 2
\problem{10} The grades of students in a large Calculus class are broken down by academic year below: \par
	\begin{table}[h]
	\centering
	\begin{tabular}{r|ccccc}
		& A & B & C & D & F \\ \hline
	Freshman & 1 & 1 & 4 & 8 & 5 \\
	Sophomore & 9 & 7 & 8 & 5 & 4 \\
	Junior & 8 & 5 & 3 & 1 & 0 \\
	Senior & 4 & 1 & 1 & 0 & 0 
	\end{tabular}
	\end{table} \par

\begin{enumerate}[(a)]
\item What is the probability that a randomly selected student received an A? 
\item What is the probability that a randomly selected student was a Freshman that failed the class?
\item What is the probability that a randomly selected student was a Sophomore or received a C?
\item What is the probability that a randomly selected student received a B, assuming that they were a Junior? 
\end{enumerate}



\newpage



% Problem 3
\problem{10} In a small neighborhood, 20 houses have a pool, 42 have a garage, and 16 have both. There are 68 houses in the neighborhood. 
	\begin{enumerate}[(a)]
	\item Find the probability that a randomly selected house has neither a pool nor a garage. 
	\item Find the probability that a randomly selected house only has a garage. 
	\item Find the probability that a randomly selected house has a pool or a garage. 
	\item Find the probability that a randomly selected house has a garage, if it has a pool. 
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Suppose that 12\% of people have a genetic abnormality. If you have a abnormality, a test will identify it 95\% of the time. However, there is an 8\% chance you will be identified as having an abnormality by the test when you do not have one. 
	\begin{enumerate}[(a)]
	\item Find the probability that a randomly selected person will test positive for a genetic abnormality. 
	\item Find the probability that a randomly selected person will test negative for a genetic abnormality. 
	\item Find the probability that a randomly selected person has a genetic abnormality and will test positive. 
	\item Find the probability that a randomly selected person has a genetic abnormality, assuming that they tested positive. 
	\end{enumerate}



\newpage



% Problem 5
\problem{10} Watch Stand-Up Math's \href{https://www.youtube.com/watch?v=7GgLSnQ48os&pp=ygUjQmF5ZXNpYW4gU3RhdGlzdGljcyB3aXRoIEhhbm5haCBGcnk\%3D}{``Bayesian Statistics with Hannah Fry''} on YouTube. Being as detailed as possible, comment on what you learned and how it relates to the course material. 


\end{document}