\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{16: Due 11/22}{Algebra is the offer made by the devil to the mathematician\dots All you need to do, is give me your soul: give up geometry.}{Michael Atiyah}

% Problem 1
\problem{10} Suppose you have a 3-day drive. You drive at an average speed of 55~mph, 65~mph, and 60~mph each day, respectively. Furthermore, you drive for 10~hours, 8~hours, and 5~hours each day, respectively. Represent your speeds each day as a vector $\mathbf{v}$ and your drive times as a vector $\mathbf{t}$. Compute $\mathbf{v} \cdot \mathbf{t}$ and interpret the result. 



\newpage



% Problem 2
\problem{10} Bill, Bob, and JoBob had a three day work week. The number of hours they worked each day, in the order listed, is represented as a column of the matrix $A$ given below. Their hourly pay, again in the order listed, is represented as a row in the column vector $\mathbf{u}$ given below. 
	\[
	A= \begin{pmatrix} 7 & 8 & 6 \\ 8 & 8 & 8 \\ 5 & 12 & 9 \end{pmatrix}, \qquad \mathbf{u}= \begin{pmatrix} 15 \\ 12 \\ 20 \end{pmatrix}
	\]
Compute $A\mathbf{u}$ and interpret the entries of the resulting vector.



\newpage



% Problem 3 
\problem{10} Assume that each of the following matrices are the reduced-row echelon form from some system of equations. For each, indicate whether there was a solution to the system or not. If there was a solution, either give the solution or give a parametrization of all possible solutions. 
	\[
	A= \begin{pmatrix} 1 & 0 & 0 & 0 & -4 \\ 0 & 1 & 0 & 0 & 3 \\ 0 & 0 & 1 & 0 & 5 \\ 0 & 0 & 0 & 1 & 0  \end{pmatrix}, \qquad B= \begin{pmatrix} 1 & 0 & 0 & 5 \\ 0 & 1 & 0 & -2 \\ 0 & 0 & 0 & 1 \end{pmatrix}, \qquad C= \begin{pmatrix} 1 & 0 & 0 & 7 \\ 0 & 1 & -2 & 5 \\ 0 & 0 & 0 & 0 \end{pmatrix}
	\]


\end{document}