\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{5: Due 10/05}{I go. You stay. No following.}{Iron Giant, Iron Giant}

% Problem 1
\problem{10} Watch the following three videos by 3Blue1Brown (Grant Sanderson):
	\begin{enumerate}[(i)]
	\item \href{https://www.youtube.com/watch?v=kYB8IZa5AuE&list=PL0-GT3co4r2y2YErbmuJw2L5tW4Ew2O5B&index=4&ab_channel=3Blue1Brown}{Linear transformations and matrices}
	\item \href{https://www.youtube.com/watch?v=XkY2DOUCWMU&list=PL0-GT3co4r2y2YErbmuJw2L5tW4Ew2O5B&index=5&ab_channel=3Blue1Brown}{Matrix multiplication as composition}
	\item \href{https://www.youtube.com/watch?v=Ip3X9LOh2dk&list=PL0-GT3co4r2y2YErbmuJw2L5tW4Ew2O5B&index=7&ab_channel=3Blue1Brown}{The determinant}
	\end{enumerate}
What did you learn from these videos? 





\newpage





% Problem 2
\problem{10} Suppose the reduced-row echelon form for an augmented matrix is the following:
	\[
	\begin{pmatrix}
	1 & -4 & 0 & 1 & 0 & 5 \\
	0 & 0 & 1 & 0 & 0 & -1 \\
	0 & 0 & 0 & 0 & 1 & 3
	\end{pmatrix}
	\]
Using this, find all the solutions to the system of equations. 





\newpage





% Problem 3
\problem{10} Can you compute the following product of matrices? If you can, compute the product. If you can not, explain why. 
	\[
	\begin{pmatrix}
	1 & -1 & 8 \\
	2 & 3 & 5 
	\end{pmatrix}
	\begin{pmatrix}
	1 & 4 \\
	0 & -6 \\
	7 & 7 \\
	-8 & 0
	\end{pmatrix}
	\]





\newpage





% Problem 4
\problem{10} Showing all your work, compute the following:
	\[
	\begin{pmatrix}
	5 & 0 & 1 \\
	-2 & -3 & 4 \\
	1 & -1 & 1
	\end{pmatrix}
	\begin{pmatrix}
	2 \\
	-1 \\
	1
	\end{pmatrix}
	\]





\newpage





% Problem 5
\problem{10} Showing all your work, compute the following:
	\[
	\begin{pmatrix}
	1 & -1 & 2 \\
	-3 & 6 & 0
	\end{pmatrix}
	\begin{pmatrix}
	0 & 4 \\
	-2 & 3 \\
	3 & -2
	\end{pmatrix}
	\]





\newpage





% Problem 6
\problem{10} Compute the determinant of the following matrix:
	\[
	\begin{pmatrix}
	2 & 1 & 5 \\
	-3 & 0 & 3 \\
	7 & 2 & 7 
	\end{pmatrix}
	\]
Is this matrix invertible? Explain. 





\newpage





% Problem 7
\problem{10} Find the inverse of the following matrix:
	\[
	\begin{pmatrix}
	2 & -1 \\
	-3 & 4
	\end{pmatrix}
	\]





\end{document}