\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{1: Due 09/11}{Everything hurts and I'm dying.}{Leslie Knope, Parks and Recreation}

% Problem 1
\problem{10} Compute the following:
	\begin{enumerate}[(a)]
	\item 47\% of 120
	\item 96\% of 55
	\item 1\% of 870
	\item 130\% of 94
	\item 285\% of 16
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Compute the following:
	\begin{enumerate}[(a)]
	\item 96 increased by 12\%
	\item 620 decreased by 24\%
	\item 45 increased by 4\% 
	\item 59 increased by 108\%
	\item 200 increased by 160\%
	\end{enumerate} 



\newpage



% Problem 3
\problem{10} You are out to dinner with your friends. The check comes and you all have decided that you will pay and they will `Venmo you.' The bill comes and it is \$187.45. You will tip the server 20\%. 
	\begin{enumerate}[(a)]
	\item What is the tip amount?
	\item What is the total bill?
	\item If you are dividing the cost equally amongst \textit{you and your four friends}, what is the amount each person should pay you?
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Suppose that Dahlia sells above ground pools. Due to inflation, she plans on raising her prices slowly. The cost of one particular above ground pool is \$3,800. Over the next three months, she will raise the price 10\%. 
	\begin{enumerate}[(a)]
	\item Calculate the price of the pool for each of the next three months. 
	\item Using your answer from (a), find by what percentage the pool price has increased. 
	\item What if she had simply raised the price of the pool by 30\%, what would the cost be?
	\item Are your final answers from (a) and (c) the same? Explain. 
	\item By what percentage should she raise the price of the pool each month if she wants the final cost to be \$4,000?
	\end{enumerate} 


\end{document}