\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{3: Due 10/06}{It's just a flesh wound.}{Black Knight, Monty Python \par and the Holy Grail}


% Problem
\problem{10} Compute the following:
\begin{enumerate}[(a)]
\item 60\% of 170
\item 20\% of 46
\item 87\% of 1698
\item 174\% of 19
\end{enumerate}



\newpage



% Problem
\problem{10} Compute the following:
\begin{enumerate}[(a)]
\item 60 increased by 20\%
\item 150 decreased by 35\%
\item 470 increased by 140\%
\item 38 decreased by 99\%
\end{enumerate}



\newpage



% Problem
\problem{10} Convert the following:
\begin{enumerate}[(a)]
\item 150,000~in to miles [5280~ft $=$ 1~mi]
\item 32~mi to km [1~mi $=$ 1.61~km; 1~km $=$ 1000~m]
\item 4~mi$^2$ to in$^2$ [1~mi $=$ 0.000189394~ft]
\end{enumerate}



\newpage



% Problem
\problem{10} Suppose you work a job where you are paid \$7.70/hr. 
\begin{enumerate}[(a)]
\item How much do you make after working 40~hours?
\item How much do you make after working 36.5~hours?
\item How many \textit{whole} hours would you have to work to make \$850?
\end{enumerate}



\newpage



% Problem
\problem{10} Suppose you work a job where you make \$9.70/hr for the first 40 regular hours you work. After that, you make time and a half, i.e. you make 50\% more per hour. 
\begin{enumerate}[(a)]
\item How much do you make if you work 35~hours in a week?
\item How much do you make if you work 45~hours in a week?
\item Suppose you start work at 8:41~am and leave at 4:32~pm. How much have you make that day?
\end{enumerate}



\newpage



% Problem
\problem{10} Suppose you work at a car dealership where you are paid on commission, i.e. you are paid based on how much you sell. The dealership pays you either a weekly salary of \$830/week or 6.7\% of whatever you sell that week---whichever is greater.
\begin{enumerate}[(a)]
\item How much are you paid if you have \$8,437.26 in sales that week?
\item How much are you paid if you have \$12,775.96 in sales that week?
\item At least how much would you have to sell (to the nearest dollar) in order to make your base-rate weekly salary?
\item Suppose you sold deck sets that cost \$245. Based on your answer from (c), how many deck sets would you have to sell each week in order to make more than your base weekly salary? 
\end{enumerate}


%\printpoints
\end{document}