\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

\newcommand{\xor}{\,\underline{\vee}\,}


% -------------------
% Content
% -------------------
\begin{document}

\homework{3: Due 09/21}{Insanity is often the logic of an accurate mind overtasked.}{Oliver Wendell Holmes, Sr.}

% Problem 1
\problem{10} Let the universe for $x$ be the set of integers. Let $P(x)$ be the predicate $P(x) \colon 10 - x < 5$ and $Q(x)$ be the predicate $Q(x) \colon x$ is a positive even integer less than 10.
	\begin{enumerate}[(a)]
	\item Find at least two values for which $P(x)$ is true and two values for which $P(x)$ is false. Do the same for $Q(x)$. 
	\item Find the truth set for $P(x)$ and find the truth set for $Q(x)$.
	\item Is it true that there is a unique $x$ in the domain such that $P(x) \wedge Q(x)$ is true? Explain.
	\item Would your answer in (c) change if the universe were instead the set of integers greater than 6? Explain. 
	\end{enumerate} 
	
	

\newpage



% Problem 2
\problem{10} Let the universe, $\mathcal{U}$, for $m, n, j, k$ be the set of integers. Define the following predicates:
	\[
	\begin{aligned}
	P(m) &\colon m \text{ is even} \\
	Q(n) &\colon n \text{ is odd} \\
	R(j) &\colon j \text{ is a perfect square} \\
	S(k) &\colon k \text{ prime} \\
	W(\ell) &\colon 1 \leq \ell \leq 10
	\end{aligned}
	\]
Write the open sentences below as complete English sentences as `simply' as possible and then determine whether the statement is true or false. If the statement is true, explain why. If not, give a counterexample. 
	\begin{enumerate}[(a)]
	\item $(\exists x) \big( Q(x) \wedge R(x) \big)$
	\item $(\forall x) \big( P(x) \vee Q(x) \big)$
	\item $(\exists! x) \big( P(x) \wedge S(x) \big)$
	\item $(\forall x) \big( P(x) \to S(x) \big)$
	\item $(\exists x) \big(R(x) \wedge W(x) \big)$
	\end{enumerate} 



\newpage



% Problem 3
\problem{10} By defining appropriate universes and predicates, quantify the open sentences below. Indicate whether the resulting statement is true or false. No justification is necessary. 
	\begin{enumerate}[(a)]
	\item For exists an integer $n$ such that $5 - 6n= 10$.
	\item For all real numbers $y$, there exists $x$ such that $2x + 3y= 4$.
	\item There exists $x$ such that for any integer $y$, $2x + 3y= 4$. 
	\item For all real numbers, if $x$ is nonnegative, then $x$ has a well defined square root. 
	\item Multiplication of real numbers is commutative. 
	\end{enumerate} 



\newpage



% Problem 
\problem{10} Let $P(x)$ be the predicate $R(x)$: $x^2 + x < 6$ and let $S(x)$ be the predicate $S(x)$: $-3 < x < 2$.  
	\begin{enumerate}[(a)]
	\item Write $\forall x \big( R(x) \to S(x) \big)$ as a complete English sentence.
	\item Write the contrapositive, converse, and negation of the open sentence in (a) as complete English sentences. 
	\end{enumerate} 


\end{document}