\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{7: Due 03/01 (02)}{Take chances, make mistakes. That's how you grow. Pain nourishes your courage. You have to fail in order to practice being brave.}{Mary Tyler Moore}

% Problem 1
\problem{10} Being as detailed as possible, answer the following:
	\begin{enumerate}[(a)]
	\item What are two measures of `center' for a dataset? 
	\item What are two measures of `variability' for a dataset?
	\item Name a measure of center which is robust and a measure of center which is not robust. 
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Stewart is tracking snowfall received over the past few days in his area. He finds the following number of inches of snow has fallen over the past few days:
	\[
	1.5" \qquad 4.2" \qquad 0" \qquad 0.8" \qquad 5.1"
	\]

\begin{enumerate}[(a)]
\item Find the mean inches of snow that fell this week.
\item Find the standard deviation for the this week's snowfall. 
\item If Stewart underestimated the inches that fell each day by 0.5", what would be the average snowfall for the week?
\end{enumerate}



\newpage



% Problem 3
\problem{10} Charlie is at a town hall meeting. He goes around the room and asks each person their age. Charlie finds the following responses for the ages of the people at the meeting:
	\[
	66 \qquad 50 \qquad 67 \qquad 40 \qquad 70 \qquad 56 \qquad 69 \qquad 57 \qquad 40 \qquad 44
	\]

\begin{enumerate}[(a)]
\item Find the median for this dataset. 
\item Find the IQR for this dataset.
\item Sketch a box and whisker plot for this dataset. 
\end{enumerate}



\newpage



% Problem 4
\problem{10} Lorelei is finding the mean of the numbers 17, 18, 26, 19. She finds that the mean is 40. By comparing Lorelei's mean as a measure of `center' to the size of the numbers, how would you explain to her why this cannot be correct. What has Lorelei done incorrectly? How would you explain to her how to fix her work? 


\end{document}