\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{10: Due 10/26}{Getting arrested, that makes people look guilty, even the innocent ones and innocent people get arrested every day.}{James (Jimmy) McGill, Better Call Saul}

% Problem 1
\problem{10} Jeffrey is writing a term paper. Currently, he has only written 8~pages. He returns from a writing break and then goes back to the paper. After an additional 5~hours of writing, he has written 20~pages. 
	\begin{enumerate}[(a)]
	\item Assuming Jeffrey writes at a constant rate, find the linear function representing the number of pages that he has written after $t$ hours of writing. 
	\item How long after this break will it take him in total to write this 50~page term paper?
	\end{enumerate} 



\newpage



% Problem 2
\problem{10} Richard is a tailor. He uses an automated sewing machine can create custom labels on jackets. Every 4~hours, it is able to stitch 26~jackets. Richard sets the machine going during the night and when he comes in the next morning it has stitched 80~jackets.
	\begin{enumerate}[(a)]
	\item Assuming the machine works at a constant rate, find the number of jackets, $J$, that the machine has stitched $t$~hours from now.
	\item How many total jackets has the machine stitched 8~hours after opening?
	\end{enumerate} 


\end{document}