\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{7: Due 03/28}{There's no such thing as a free lunch.}{Milton Friedman}

% Problem 1
\problem{10} Ms. Currant invests a principal of \$3,500 in an account with 8.5\% per year simple interest.
	\begin{enumerate}[(a)]
	\item How much interest has accumulated after 20~months?
	\item How much is the investment worth after 20~months?
	\item How long until the investment is worth \$4,200?
	\item How long until the investment has doubled in value?
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Colonel Tumeric takes out a short-term loan of \$680. The bank issues a 9\% discount loan for 90~days.
	\begin{enumerate}[(a)]
	\item What is the maturity?
	\item What are the discount and proceeds?
	\item How much is owed after 90~days and how much is paid in total?
	\item What are the nominal and effective interest rates?
	\end{enumerate}



\newpage



% Problem 3
\problem{10} Professor Mauve invests her money with an investment startup that promises interest returns of 3.5\% per year, compounded semiannually. Suppose she initially invests \$8,000.  
	\begin{enumerate}[(a)]
	\item How much is the investment worth in 3~years?
	\item How long until the investment is worth \$10,000?
	\item How much should she have invested to have \$10,000 after 3~years?
	\item Find the effective interest rate.
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Mrs. Cobalt takes out a loan of \$400,000 at a yearly interest rate of 1.5\%, compounded continuously. 
	\begin{enumerate}[(a)]
	\item How much is owed on the loan after 3~years?
	\item How long until \$500,000 is owed on the loan?
	\item How much should the loan have been for if she planned on paying \$600,000 after 5~years?
	\item Find the effective interest rate.
	\end{enumerate}


\end{document}