\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{false} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{14: Due 12/12}{It is a curious historical fact that modern quantum mechanics began with two quite different mathematical formulations: the differential equation of Schr\"odinger and the matrix algebra of Heisenberg. The two apparently dissimilar approaches were proved to be mathematically equivalent.}{Richard Feynman}

% Problem 1
\problem{10} Find the augmented matrix to the corresponding system of equations:
	\[
	\begin{gathered}
	x - 2y + 3z - w= 10 \\
	x + 4y - 26w= 19 \\
	-6x + 19z + w= 25
	\end{gathered}
	\] \pspace

\sol First, we order the variables as $x$, $y$, $z$, and then $w$. We also make sure each equality has all variables present. This gives us the following system of equations:
	\[
	\begin{gathered}
	x - 2y + 3z - w= 10 \\
	x + 4y + 0z - 26w= 19 \\
	-6x + 0y + 19z + w= 25
	\end{gathered}
	\]
Therefore, the augmented matrix is\dots
	\[
	\begin{pmatrix}
	1 & -2 & 3 & -1 & 10 \\
	1 & 4 & 0 & -26 & 19 \\
	-6 & 0 & 19 & 1 & 25
	\end{pmatrix}
	\]



\newpage



% Problem 2
\problem{10} The matrix below is the initial augmented matrix for a system of linear equations. Find the system of linear equations. 
	\[
	\begin{pmatrix}
	5 & -3 & 1 & 8 \\
	1 & 0 & -1 & 5 \\
	-6 & 2 & 9 & 1 \\
	5 & 6 & 7 & 12
	\end{pmatrix}
	\] \pspace

\sol Each column corresponds to a variable in the system---except the last column that corresponds to the `other side' of the equalities. Therefore, there are $4 - 1= 3$ variables in the system, which we will label $x, y, z$. Therefore, the system of equations must be\dots
	\[
	\begin{aligned}
	5x - 3y + z&= 8 \\
	x - z&= 5 \\
	-6x + 2y + 9z&= 1 \\
	5x + 6y + 7z&= 12
	\end{aligned}
	\]



\newpage



% Problem 3
\problem{10} The following matrix is the RREF of an augmented matrix coming from a system of equations. Did this system of equations have a solution? If the system of equations had a solution, find all the possible solutions. If the system did not have a solution, explain why. 
	\[
	\begin{pmatrix}
	1 & 0 & 0 & 0 & 0 & 0 \\
	0 & 1 & 0 & 0 & 0 & -5 \\
	0 & 0 & 0 & 1 & -2 & 7 \\
	0 & 0 & 0 & 0 & 0 & 0 
	\end{pmatrix}
	\] \pspace

\sol Each of the columns of the matrix corresponds to a variable---except for the last column which corresponds to the `other' side of the equalities. There are then $6 - 1= 5$~variables. We mark the pivot columns of the matrix: 
	\[
	\begin{pmatrix}
	\boxed{1} & 0 & 0 & 0 & 0 & 0 \\
	0 & \boxed{1} & 0 & 0 & 0 & -5 \\
	0 & 0 & 0 & \boxed{1} & -2 & 7 \\
	0 & 0 & 0 & 0 & 0 & 0 
	\end{pmatrix}
	\]
Therefore, $x_1, x_2, x_4$ will be `fixed.' We then take $x_3, x_5$ to be free variables. The first row tells us that $x_1= 0$. The second row tells us that $x_2= -5$. The third row tells us that $x_4 - 2x_5= 7$, which implies that $x_4= 2x_5 + 7$. Therefore, the solution is\dots
	\[
	\begin{cases}
	x_1= 0 \\
	x_2= -5 \\
	x_3 \colon \text{ free} \\
	x_4= 2x_5 + 7 \\
	x_5 \colon \text{ free}
	\end{cases}
	\]



\newpage



% Problem 4
\problem{10} The following matrix is the RREF of an augmented matrix coming from a system of equations. Did this system of equations have a solution? If the system of equations had a solution, find all the possible solutions. If the system did not have a solution, explain why. 
	\[
	\begin{pmatrix}
	1 & 0 & -9 \\
	0 & 1 & 0 
	\end{pmatrix}
	\] \pspace

\sol Each of the columns of the matrix corresponds to a variable---except for the last column which corresponds to the `other' side of the equalities. There are then $3 - 1= 2$~variables. From the first row, we see that $x_1= -9$. From the second row, we see that $x_2= 0$. Therefore, the unique solution is $(x_1, x_2)= (0, 0)$, i.e. \dots
	\[
	\begin{cases}
	x_1= 0 \\
	x_2= 0
	\end{cases}
	\]



\newpage



% Problem 5
\problem{10} The following matrix is the `RREF' of an augmented matrix coming from a system of equations. Did this system of equations have a solution? If the system of equations had a solution, find all the possible solutions. If the system did not have a solution, explain why. 
	\[
	\begin{pmatrix}
	1 & 0 & 0 & 0 & 1 \\
	0 & 1 & 0 & 0 & 2 \\
	0 & 0 & 1 & 0 & 3 \\
	0 & 0 & 0 & 1 & 4 \\
	0 & 0 & 0 & 0 & 5 
	\end{pmatrix}
	\] \pspace

\sol The last row of the matrix implies that $0= 5$. Therefore, there is no solution to the system of equations. 


\end{document}