\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{14: Due 12/12}{It is a curious historical fact that modern quantum mechanics began with two quite different mathematical formulations: the differential equation of Schr\"odinger and the matrix algebra of Heisenberg. The two apparently dissimilar approaches were proved to be mathematically equivalent.}{Richard Feynman}

% Problem 1
\problem{10} Find the augmented matrix to the corresponding system of equations:
	\[
	\begin{gathered}
	x - 2y + 3z - w= 10 \\
	x + 4y - 26w= 19 \\
	-6x + 19z + w= 25
	\end{gathered}
	\]



\newpage



% Problem 2
\problem{10} The matrix below is the initial augmented matrix for a system of linear equations. Find the system of linear equations. 
	\[
	\begin{pmatrix}
	5 & -3 & 1 & 8 \\
	1 & 0 & -1 & 5 \\
	-6 & 2 & 9 & 1 \\
	5 & 6 & 7 & 12
	\end{pmatrix}
	\]



\newpage



% Problem 3
\problem{10} The following matrix is the RREF of an augmented matrix coming from a system of equations. Did this system of equations have a solution? If the system of equations had a solution, find all the possible solutions. If the system did not have a solution, explain why. 
	\[
	\begin{pmatrix}
	1 & 0 & 0 & 0 & 0 & 0 \\
	0 & 1 & 0 & 0 & 0 & -5 \\
	0 & 0 & 0 & 1 & -2 & 7 \\
	0 & 0 & 0 & 0 & 0 & 0 
	\end{pmatrix}
	\]



\newpage



% Problem 4
\problem{10} The following matrix is the RREF of an augmented matrix coming from a system of equations. Did this system of equations have a solution? If the system of equations had a solution, find all the possible solutions. If the system did not have a solution, explain why. 
	\[
	\begin{pmatrix}
	1 & 0 & -9 \\
	0 & 1 & 0 
	\end{pmatrix}
	\]



\newpage



% Problem 5
\problem{10} The following matrix is the `RREF' of an augmented matrix coming from a system of equations. Did this system of equations have a solution? If the system of equations had a solution, find all the possible solutions. If the system did not have a solution, explain why. 
	\[
	\begin{pmatrix}
	1 & 0 & 0 & 0 & 1 \\
	0 & 1 & 0 & 0 & 2 \\
	0 & 0 & 1 & 0 & 3 \\
	0 & 0 & 0 & 1 & 4 \\
	0 & 0 & 0 & 0 & 5 
	\end{pmatrix}
	\]


\end{document}