\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{3: Due 02/16}{This is not a dictatorship. This is America. Give me liberty, or give me meth.}{Frank Gallagher, Shameless}

% Problem 1
\problem{10} Determine if the point $(x, y)= (-1, 3)$ is a solution to the system of equations below. Be sure to fully justify your answer.
	\[
	\begin{aligned}
	x^2 + xy + y&= 1 \\
	x^3 - y^3&= -26
	\end{aligned}
	\]



\newpage



% Problem 2
\problem{10} Determine if the linear system of equations below has none, one, or infinitely many solutions. Be sure to fully justify your answer. 
	\[
	\begin{aligned}
	2x - y&= -2 \\
	3x + 5y&= 10
	\end{aligned}
	\]



\newpage



% Problem 3
\problem{10} Find the coefficient matrix, solution vector, and augmented matrix associated with the system of equations below. 
	\[
	\begin{aligned}
	5x_1 + x_2 - 6x_3&= 19 \\
	3x_2 - 2x_3&= -6 \\
	9x_1 + 8x_3&= 5
	\end{aligned}
	\]



\newpage



% Problem 4
\problem{10} Write the system of equations associated to the augmented matrix below. 
	\[
	\begin{pmatrix}
	6 & 1 & -5 & -7 \\
	4 & 0 & -1 & 9 \\
	1 & 1 & 1 & 4 \\
	\end{pmatrix}
	\]



\newpage



% Problem 5
\problem{10} Find all the pivot positions in the augmented matrix below. Also, determine if the system of equations is consistent or not. 
	\[
	\begin{aligned}
	\begin{pmatrix}
	1 & 4 & 6 & -2 & 5 \\
	0 & 0 & -1 & 7 & 12 \\
	0 & 0 & 0 & -9 & 5 \\
	0 & 0 & 0 & 0 & 1
	\end{pmatrix}
	\end{aligned}
	\]



\newpage



% Problem 4
\problem{10} The matrix below represents a reduced-row echelon form of augmented matrix for a system of equations. Determine the solutions to this original system of equations. 
	\[
	\begin{aligned}
	\begin{pmatrix}
	1 & 0 & 0 & -5 \\
	0 & 1 & 0 & 3 \\
	0 & 0 & 1 & 4
	\end{pmatrix}
	\end{aligned}
	\]



\newpage



% Problem 5
\problem{10} Solve the following system of equations using elimination. Then solve the system of equations again by creating an augmented matrix and find its reduced-row echelon form.
	\[
	\begin{aligned}
	x - 3y&= -9 \\
	-2x + y&= 8
	\end{aligned}
	\]



\newpage



% Problem 5
\problem{10} Use \href{https://www.wolframalpha.com/}{WolframAlpha's} \texttt{RowReduce} to find the solution to the following system of equations: 
	\[
	\begin{aligned}
	x_1 + x_2 + x_3 + x_4&= 1 \\
	x_1 - 2x_2 + 3x_3 - 4x_4&= 2 \\
	10x_1 + 3x_2 - 5x_3 - 2x_4&= 3 \\
	-2x_1 - 4x_2 + 6x_3 + 8x_4&= 4
	\end{aligned}
	\]


\end{document}