\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{9: Due 11/16}{What I hear when I'm being yelled at is people caring loudly at me.}{Leslie Knopp, Parks and Recreation}

% Problem 1
\problem{10} Otto Graf borrows \$8,000 from a neighbor to help fund his startup. He promises to pay back the neighbor, plus 15\% interest per year on the borrowed amount. 
\begin{enumerate}[(a)]
\item What is the interest owed at the end of 9~months?
\item How much does Otto owe the neighbor if he pays them back after a year and a half? How much of this payment was interest?
\item Suppose Otto wants to be sure he does not owe the neighbor more than \$10,000. If he plans on repaying them in 2~years, what is the largest sum of money that he can borrow from them? 
\end{enumerate}





\newpage





% Problem 2
\problem{10} Mary A. Richman takes out a \$600 loan from the bank. Because of her credit history, she is charged a 6\% discount on a six month note. 
\begin{enumerate}[(a)]
\item What are the nominal and effective interest rates for this loan?
\item What is the discount of this loan?
\item How much money does Mary receive from the bank?
\item How much does Mary owe the bank after six months?
\end{enumerate}





\newpage





% Problem 3
\problem{10} Paige Turner invests \$3,500 in a social media marketing company that promises a 4.1\% annual return on the investment, with interest paid to the investors semiannually. 
\begin{enumerate}[(a)]
\item What is the nominal and effective interest rate for this investment?
\item How much money will the investment be worth after 2~years?
\item How long until the investment is worth \$5,000?
\item How much should Paige have placed in the company if she wanted \$5,000 at the end of 2 years? 
\end{enumerate}





\newpage





% Problem 4
\problem{10} Adam Baum deposits \$18,500 into a savings account that pays 2.2\% annual interest, compounded continuously. 
\begin{enumerate}[(a)]
\item What is the nominal and effective interest rate for this account?
\item How much money will be in the account after 10~years?
\item How long until the account has \$20,000? 
\item How much should Mr. Baum have placed in the account if he wanted \$20,000 at the end of 5 years? 
\end{enumerate}


\end{document}