\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{Interest \& Probability}

% Problem 1
\problem If you deposit \$12,000 into a savings account that earns 6.6\% annual interest, compounded monthly, find the amount in the savings account after 4~years. How much interest have you earned? \pspace

% Problem 2
\problem Suppose you take out a 5-year loan for \$8,500 at 4.2\% annual interest, compounded semiannually. How much do you owe at the end of the loan? How much interest did you pay? \pspace

% Problem 3
\problem Suppose you place \$500 into an account that earns 5.1\% annual interest, compounded daily. How long until you have saved \$600? \pspace

% Problem 4
\problem Suppose you take out a loan for \$7,000 at 7.9\% annual interest, compounded quarterly. How long until you owe \$10,000? \pspace

% Problem 5
\problem You have a rabbit farm with 45 rabbits. Their colors, broken down by the sex of the rabbit, are summarized below.
	\begin{table}[!ht]
	\centering
	\begin{tabular}{|c|c|c|} \hline
	& White & Brown \\ \hline
	Male &10 & 15 \\ \hline
	Female & 8 & 12 \\ \hline
	\end{tabular}
	\end{table}

\begin{enumerate}[(a)]
\item What percentage of the rabbits are female?
\item What percentage of the rabbits are white?
\item What percentage of the rabbits are white and male?
\item What percentage of the rabbits are brown or female?
\item What percentage of the female rabbits are brown?
\end{enumerate} \pspace

% Problem 6
\problem The table below classifies a group of voters according to sex and political affiliation. 
	\begin{table}[!ht]
	\centering
	\begin{tabular}{|c|c|c|c|} \hline
	& Democrat & Republican & Independent \\ \hline
	Male &110 & 180 & 240 \\ \hline
	Female & 150 & 130 & 190 \\ \hline
	\end{tabular}
	\end{table}

\begin{enumerate}[(a)]
\item What is the probability that a voter was male?
\item What is the probability that a voter was Republican?
\item What is the probability that a voter was a male Democrat?
\item What is the probability that a voter was female or Independent?
\item What is the probability that a voter was an Independent, assuming that they were male?
\end{enumerate} \pspace

% Problem 7
\problem A programming class has 50 students, 14 students had some familiarity with Python but not C\#, 8 students had familiarity with C\# but not Python, and 12 students had familiarity with both.
	\begin{enumerate}[(a)]
	\item What percentage of students had seen Python or C\#?
	\item What percentage of students had only seen C\#?
	\item What percentage of students had seen Python and C\#?
	\item What percentage of students had seen neither Python nor C\#?
	\item What percentage of students had seen only Python or neither programming language?
	\item What percentage of students that had seen C\# had also seen Python?
	\end{enumerate} \pspace

% Problem 8
\problem Suppose that 60 people are interviewed about the electronics that they own. Of the people interviewed, 40 say that they own a laptop, 25 say they own a desktop, and 10 say that they have both.
	\begin{enumerate}[(a)]
	\item What is the probability that a randomly selected person owns only a laptop?
	\item What is the probability that a randomly selected person owns only a desktop?
	\item What is the probability that a randomly selected person owns both a laptop and a desktop?
	\item What is the probability that a randomly selected person owns neither a desktop or a laptop?
	\item What is the probability that a randomly selected person that owns a laptop also owns a desktop?
	\end{enumerate}


\end{document}