\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{5: Due 09/22}{Be aware of little expenses. A small leak will sink a great ship.}{Benjamin Franklin}

% Problem 1
\problem{10} Joy Rider is trying to save for college. At the end of each month, she places \$300 into an account that earns 4.6\% yearly annual interest, compounded monthly. If she does this for 4~years, how much has she saved for college?



\newpage



% Problem 2
\problem{10} Oren Jellow owns a produce distribution company. To plan ahead, every 3~months, he makes a deposit at the beginning of the month, so that he will eventually have enough saved to replace a delivery truck. The money is placed into an account earning 3.8\% annual interest, compounded quarterly. If he anticipates having to replace a truck every 5~years and the trucks cost \$85,000 to replace, how much money should he deposit each time?



\newpage



% Problem 3
\problem{10} Sara Bellum is setting aside money for her nephew's HS graduation in 2~years. At the start of each month, she places \$20 into an account that earns 1.8\% yearly annual interest, compounded semiannually. How much will be she be giving her nephew at the end of the 2~years?



\newpage



% Problem 4
\problem{10} Sonny Day is saving for a down payment on a condo. He wants to have \$35,000 saved in the next 5~years. So at the end of each month, he will make a deposit into an account that earns 3.7\% annual interest, compounded daily. How much should he make the monthly deposit?

\end{document}

FV, simple ord annuity
Payment, simple annuity due
FV, general annuity due
PV, general ord annuity