\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{3: Due 02/15 (16)}{For the things we have to learn before we can do them, we learn by doing them.}{Aristotle}

% Problem 1
\problem{10} A box of candy contains 30~different pieces of candy. Of these pieces, 10 are filled with chocolate, 10 are filled with nougat, and 6 are filled with both. 
	\begin{enumerate}[(a)]
	\item How many ways can you select a candy that contains chocolate or nougat?
	\item How many pieces of candy contain neither chocolate nor nougat?
	\item How many ways can you select a candy that is filled with chocolate or something other than chocolate or nougat?
	\end{enumerate} 



\newpage



% Problem 2
\problem{10} A restaurant has a breakfast special. The special consists of a selection of a sandwich, a side, and some beverage. The restaurant offers 5 different breakfast sandwiches, 8 different sides, and 3 different beverages. You must choose two different sides. How many possible breakfast orders are there? 



\newpage



% Problem 3
\problem{10} Showing all necessary work, compute the following:
	\begin{enumerate}[(a)]
	\item $8!$
	\item $0!$
	\item $_9P_2$
	\item $\binom{6}{4}$
	\item $_{15}C_3$
	\end{enumerate}



\newpage



% Problem 4
\problem{10} There are 19 students in a homeroom. Of these students, 8 are in choir, 5 are in orchestra, and 1 is in both. A student claims That there are $8 + 1= 9$ students in choir and that there are a total of 5 students that are in neither orchestra nor choir. Is the student correct? Explain. 


\end{document}