\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{17: Due 01/19}{I found out that smoking is the leading cause of statistics.}{Matthew Gray Gubler}

% Problem 1
\problem{10} Consider the following dataset: \par
	\begin{table}[h]
	\centering
	\begin{tabular}{rrrrrrrrrrr}
	$9$ & $-8$ & $13$ & $-1$ & $0$ & $1$ & $23$ & $2$ & $5$ & $10$ & $20$ \\
	$-10$ & $4$ & $9$ & $12$ & $3$ & $8$ & $15$ & $10$ & $-1$ & $6$ & $17$ 
	\end{tabular}
	\end{table} \par

\begin{enumerate}[(a)]
\item Find the 5-number summary for this dataset. 
\item Find the IQR for this dataset. 
\item Sketch a box plot of this dataset. 
\end{enumerate}



\newpage



% Problem 2
\problem{10} Consider the following dataset:
	\[
	-2 \qquad 0 \qquad 1 \qquad 1 \qquad 5 \qquad 8
	\]

\begin{enumerate}[(a)]
\item Find the mean for this dataset. 
\item Find the standard deviation for this dataset. 
\end{enumerate}



\newpage



% Problem 3
\problem{10} Consider the probability space whose events, $X$, and probabilities, $P(X)$, are given below: \par
	\begin{table}[h]
	\centering
	\begin{tabular}{r||cccc}
	$X$ & $1$ & $2$ & $3$ & $4$ \\ \hline \rule[-1.5ex]{0pt}{5ex}
	$P(X)$ & $\dfrac{2}{10}$ & $\dfrac{1}{10}$ & $\dfrac{4}{10}$ & ? 
	\end{tabular}
	\end{table} \par

\begin{enumerate}[(a)]
\item Find $P(4)$.
\item Find the expected value of $X$. 
\end{enumerate}



\newpage



% Problem 4
\problem{10} There is an approximately 1 in 300~million chance of winning the lottery. Suppose that the average jackpot amount for the lottery is 800~million. After taking the lump sum, the `take home' amount for an 800~million jackpot prize is about 500~million. A lottery ticket costs \$2. 
	\begin{enumerate}[(a)]
	\item Compute the expected value for the lottery. 
	\item Based on (a), should you play the lotto? 
	\end{enumerate}



\newpage



% Problem 5
\problem{10} Watch Zach Star's \href{https://www.youtube.com/watch?v=bVG2OQp6jEQ&t=933s&pp=ygUtVGhpcyBpcyBIb3cgRWFzeSBJdCBpcyB0byBMaWUgd2l0aCBTdGF0aXN0aWNz}{``This is How Easy It is to Lie with Statistics''} on YouTube. Being as detailed as possible, comment on what you learned and how it relates to the course material. 


\end{document}