\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{4: Due 02/07}{Oh my! It smells like Granda's house at Christmas. That's when we found her dead on the toilet.}{Kenneth Parcell, 30 Rock}

% Problem 1
\problem{10} Eileen Bach sells propane and propane accessories. She wants to start a YouTube channel where she reviews grills. Of course, she will then have to regularly purchase grills. She wants to review a grill per week and post it to her channel. Eileen estimates that the average grill will cost her \$720. After she is done, she thinks that she will be able to re-sell the grill at a 40\% discount. She plans on saving for 3~months worth of reviews by making a single deposit into an account that earns 1.13\% annual interest, compounded every other month for a period of a year and a half. 
	\begin{enumerate}[(a)]
	\item At the end of the month, how much should Eileen estimate that she has net spent on grills?
	\item How much should she deposit into the account? 
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Susan Flaye has taken out a loan to afford the best possible broom she can to join her local adult Quidditch league. The loan was for \$870 at 9.55\% annual interest, compounded quarterly. She has not made any payments on the loan for the past 2~years. Though Susan has performed fantastically on her team---leading them to over 13 victories---how much does Susan currently owe on her loan?



\newpage



% Problem 3
\problem{10} Ty Coon is saving to build a roller coaster park. Though he has investors and can take out loans, he wants to have at least \$26~million saved to bring to the table on his own when the park opens. Ty will deposit money into an account that earns 2.9\% annual interest, compounded continuously. The money will sit for 3~years while the park is being constructed. What is the minimum amount that Ty should deposit now to have at least \$26~million at the end of the three years?



\newpage



% Problem 4
\problem{10} Justin Caese has invested in his future by purchasing the world's largest Pog collection. He currently estimates that the collection is worth \$5,600 and that the value increases each month by 1.17\%.
	\begin{enumerate}[(a)]
	\item How much is the collection worth in 10~years?
	\item How long until the collection is worth \$100,000?
	\end{enumerate}


\end{document}