\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{6: Due 10/02}{I see the muscle shirt came today. Muscles coming tomorrow? Did ya' get a tracking number? Oh, I hope he got a tracking number.}{Daryl, Letterkenny}

% Problem 1
\problem{10} Showing all your work, compute the following:
	\begin{enumerate}[(a)]
	\item 83\% of 1,295
	\item 3\% of 920
	\item 99\% of 67
	\item 165\% of 81
	\item 20\% of 45.30
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Showing all your work, compute the following:
	\begin{enumerate}[(a)]
	\item 560 increased by 4\%
	\item 357 decreased by 23\%
	\item 993 decreased by 95\%
	\item 55 increased by 105\%
	\item 89.4 increased by 224\%
	\end{enumerate}



\newpage



% Problem 3
\problem{10} Your biology class course grade is determined by the following components: \par
	\begin{table}[h]
	\centering
	\begin{tabular}{lr}
	Homeworks & 30\% \\
	Labs & 20\% \\
	Midterm & 20\% \\
	Final & 20\% \\
	Project & 10\% \\
	\end{tabular}
	\end{table} \par
Suppose that your homework average was 86\%, your lab average was 75\%, your midterm average was 68\%, your final grade was 81\%, and your project grade was 92\%. 
	\begin{enumerate}[(a)]
	\item Compute your course average.
	\item If the final exam had not yet occurred, i.e. you had not yet received the 81\%, but all the other course grades were as listed above, then what is your current course average?
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Suppose you received the following grades this semester: \par
	\begin{table}[h]
	\centering
	\begin{tabular}{lrc}
	Course & Credits & Grade \\ \hline
	CS 320: Ethics in a Technological Society & 3 & C+ \\
	CS 380: Networking & 4 & B+ \\
	CS485: Web Programming & 3 & B-- \\
	CS 424: Data Mining & 3 & A-- \\
	ECON 101: Principles of Macroeconomics & 3 & A\phantom{--}
	\end{tabular}
	\end{table} \par
Given the following grade values, 
	\begin{table}[h]
	\centering
	\begin{tabular}{lrclr}
	Grade & Values & & Grade & Values \\ \hline
	A & 4.0 & \hspace{1cm} & C+ & 2.3 \\
	A-- & 3.7 & & C & 2.0 \\
	B+ & 3.3 & & C-- & 1.7 \\
	B & 3.0 & & D & 1.0 \\
	B-- & 2.7 & & F & 0
	\end{tabular}
	\end{table}

\begin{enumerate}[(a)]
\item Compute your semester GPA. 
\item If your previous GPA based on 76 credits was 3.012, what is your current overall GPA?
\end{enumerate}


\end{document}