\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

\newcommand{\blank}[1]{\underline{\hspace{#1}}} % Blank Underline

% -------------------
% Content
% -------------------
\begin{document}

\homework{15: Due 11/14}{One reason why Combinatorics has been slow to become accepted as part of mainstream Mathematics is the common belief that it consists of a bag of isolated tricks, a number of areas\dots with little or no connexion between them. We shall see that they have numerous threads weaving them together into a beautifully patterned tapestry.}{Richard K. Guy}

% Problem 1
\problem{10} Showing all your work, complete the following:
	\begin{enumerate}[(a)]
	\item Writing $\left(3x^2 - \frac{1}{x} \right)^{12}$ in descending power of $x$, find the `middle' term. 
	\item Find the coefficient of $x^3y^2$ in $(2x - 3y)^5$.
	\item Find the coefficient of $x^2yz^3$ in $(2x - y + 3z)^6$
	\end{enumerate}



\newpage



% Problem 2
\problem{10} If you distribute 27 tasks amongst 6 people, what is the maximum number of tasks a person can be assigned? What is the minimum number of tasks someone can be assigned to? Does there have to be a person with at at least 5 tasks assigned to them? Explain. Does there have to be a person with at most 4 tasks assigned to them? Explain. 



\newpage



% Problem 3
\problem{10} Consider the set of positive integers less than 10,000. How many of these numbers are\dots
	\begin{enumerate}[(a)]
	\item \dots divisible by 5 or 7?
	\item \dots divisible by 2 and 5 but not 20?
	\item \dots divisible by 2, 3, or 5?
	\end{enumerate}


\end{document}