\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,bmargin=1in,tmargin=1in]{geometry}
\usepackage{style}

\pagenumbering{gobble}


% -------------------
% Content
% -------------------
\begin{document}

% TItle
\begin{center} 
\bfseries
\color{stacred}
\LARGE Syllabus Quick Facts \par\vspace{0.2\baselineskip}
\Large MATH 104: Pre-Calculus Mathematics --- Spring 2024
\end{center} \pspace


% Course Information
\mysection{0.27}{Course Information}{course_info}
\hspace{0.53cm} {\itshape Instructor Email}: \href{mailto:cmcwhort@stac.edu}{cmcwhort@stac.edu} \par
\hspace{0.53cm} {\itshape Course Webpage}: \href{https://coffeeintotheorems.com/courses/2024-2/spring/math-104/}{https://coffeeintotheorems.com/courses/2024-2/spring/math-104/} \par
\hspace{0.53cm} {\itshape Office Hours}: 	\par \vspace{-0.3cm}
	\begin{table}[!ht]
	\centering
	\begin{tabular}{l || l}
	Mon. & 11:30~am -- 12:30~pm \\
	Tues. & 11:30~am -- 12:30~pm \\
	Wed. & 11:30~am -- 12:30~pm \\
	Thurs. & 11:30~am -- 12:30~pm \\
	\end{tabular}
	\end{table} \pspace


% Grading Components
\mysection{0.27}{Grading Components}{grade_comp}
Course grades are determined by the following components: \par \vspace{-0.3cm}
	\begin{table}[!ht]
        \begin{tabular}{clr}
        & Classwork & 10\% \\
        & Homework & 20\% \\
	& Quizzes & 10\% \\
	& Exams & 60\% 
        \end{tabular} 
        \end{table} \sectionbreak


% Attendance 
\mysection{0.27}{Attendance}{attendance}
Attend each lecture and show up on time. Anticipated absences should be addressed with the instructor in advance of the absence. Address any absences---anticipated or otherwise---with the instructor. If you miss a lecture, you are responsible for any material covered, any work assigned, any course changes made, etc. during the class. Four or more unexcused absences from lectures could result in receiving a grade penalty per additional absence or an `F' in the course. Furthermore, excessive lateness will also count as an absence. \pspace
\sectionbreak

% Quizzes 
\mysection{0.27}{Quizzes}{quizzes}
There will be a quiz \textit{every} class, typically at the start of class. Because solutions will often then be immediately discussed, no make-up quizzes will be given (except under extraordinary circumstances). \sectionbreak



% Homework
\mysection{0.30}{Homework \& Classwork}{homeworks}
Homeworks are essential for learning course material and will be what you spend most of your outside time doing. Extensions on these homeworks may be possible. However, requests for extensions should be made at least 24-hours in advance, if at all possible. Any extensions, due dates, and grade penalties for late assignments will be determined by the instructor on a student-by-student basis. 



\newpage



{\itshape\bfseries\color{stacred}Classwork.} Because attendance and participation is essential to the learning process, there will be graded classwork each class. These assignments can be found on MyOpenMath, linked on the Canvas course page. Typically, these assignments will be worked on during class. An individual's problems may be different than the exact one done in class. If these problems are not worked on during class, the problems are not finished during lecture, or you are absent, every student is expected to complete and submit the classwork assigned each lecture. These will typically be due the day after lecture. Should you need to miss class, be sure to complete these assignments! \pspace

{\itshape\bfseries\color{stacred}Homework.} The majority of course homework will be done using an online homework system through MyOpenMath, which is linked on the course Canvas page. This is also where one of the course text references can be found. However, other assignments may be given during the course. Be sure to start assignments early and work through problems carefully, being sure to work out solutions in your notes in full to best support your learning. Should you have difficulty accessing the assignments, formatting your answers, or submitting your assignments, please, do not wait until the last minute to contact the instructor! \sectionbreak



% Exams
\mysection{0.27}{Exams}{exams}
There will be three exams in this course, each worth 20\% of the total course grade for a total of 60\% of the course grade. The tentative schedule for these exams can be found below. You should be present, seated, and prepared for a scheduled exam before the exam begins. If you are late, you should not expect extra exam time. There are no make-up exams except under extraordinary circumstances. \sectionbreak



% Course Schedule 
\mysection{0.27}{Course Schedule}{schedule}
The following is a \emph{tentative} schedule for the course and is subject to change. 
	\begin{table}[!ht]
        \centering
        \scalebox{1}{%
        \begin{tabular}{ll || ll}
        Date & Topic(s) & Date & Topic(s) \\ \hline 
	01/23 & Order of Operations & 03/14 & Spring Break \\
	01/25 & Scatterplots & 03/19 & GCF \& Grouping \\
	01/30 & Slope \& Rate of Change & 03/21 & GCF \& Grouping \\
	02/01 & Interpreting Slope & 03/26 & Zero-Product Property \\
	02/06 & Slope-Intercept Form & 03/28 & Exponential Functions \\
	02/08 & Point-Slope Form & 04/02 & Exam 2 \\
	02/13 & Regression & 04/04 & Logarithms \\
	02/15 & Quadratics & 04/09 & Logarithms \\
	02/20 & Exam 1 & 04/11 & Logarithms \\
	02/22 & Scientific Notation & 04/16 & Exponential Equations \\
	02/27 & Exponent Rules & 04/18 & Logarithmic Equations \\
	02/29 & Fractional Exponents & 04/23 & Exponential/Log Models \\
	03/05 & Polynomials & 04/25 & Additional Topics/Review \\
	03/07 & FOIL & 04/30 & Review \\
	03/12 & Spring Break & 05/02 & Exam 3
        \end{tabular}
        }
        \end{table}


\end{document}