\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{19: Due 12/10}{It's about time somebody stood up to Auntie Eleanor. But you, not me. Oh, god! She can't ever know I was here.}{Oliver T'sien, Crazy Rich Asians}

% Problem 1
\problem{10} Suppose you invest \$1500 in an account which gains 6\% annual interest compounded monthly. 
        \begin{enumerate}[(a)]
        \item Determine the amount of money in the account after 8~years.
        \item How long until the account has \$4000?
        \item How much should you place in the account if you want to have \$2000 saved after 3~years?
        \end{enumerate} \pspace





\newpage





% Problem 2
\problem{10} Suppose you invest \$430 in an account which gains 4\% annual interest compounded semiannually. 
        \begin{enumerate}[(a)]
        \item Determine the amount of money in the account after 2~years.
        \item How long until the account has \$1000?
        \item How much should you place in the account if you want to have \$600 saved after 5~years?
        \end{enumerate} \pspace





\newpage





% Problem 3
\problem{10} Suppose you invest \$600 in an account which gains 5\% annual interest compounded continuously. 
        \begin{enumerate}[(a)]
        \item Determine the amount of money in the account after 3~years.
        \item How long until the account has \$800?
        \item How much should you place in the account if you want to have \$900 saved after 10~years?
        \end{enumerate} \pspace





\newpage





% Problem 4
\problem{10} Suppose you invest \$3000 in an account which gains 2\% annual interest compounded continuously. 
        \begin{enumerate}[(a)]
        \item Determine the amount of money in the account after 7~years.
        \item How long until the account has \$3500?
        \item How much should you place in the account if you want to have \$3700 saved after 4~years?
        \end{enumerate} \pspace


%\printpoints
\end{document}