\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

\newcommand{\blank}[1]{\underline{\hspace{#1}}} % Blank Underline

% -------------------
% Content
% -------------------
\begin{document}

\homework{14: Due 11/14}{Every hard problem in mathematics has something to do with combinatorics.}{Lennart Carleson}

% Problem 1
\problem{10} Lord of the Wings is a food truck that has a number of offerings: 8 types burgers, 6~types of wings, 5~types of fries, 3~types of wraps, and 4~types of sides. 
	\begin{enumerate}[(a)]
	\item How many ways can you order one thing from the menu? [Ans: 26]
	\item How many ways can you order two different things from the menu? [Ans: 325]
	\item If you will order a meal consisting of a burger/wing/wrap, a fry, and a side, how many possible orders are there? [Ans: 340]
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Showing all your work, compute the following:
	\begin{enumerate}[(a)]
	\item $\binom{12}{3}$
	\item $_{120} P_5$
	\item $7!$
	\item $_{9} C_{7}$
	\item $\binom{10}{2,5,3}$
	\end{enumerate}



\newpage



% Problem 3
\problem{10} A standard deck of cards consists of 52~cards: four suits of spades, hearts, diamonds, and clubs. Each suit consists of 13~cards: 2, 3, $\ldots$, 9, 10, jack, queen, king, and ace. A six-card game begins with each player being dealt six cards. 
	\begin{enumerate}[(a)]
	\item How many possible hands can you begin with? [Ans: 20,358,520]
	\item How many ways can you be dealt exactly two face cards? [Ans: 6,031,740]
	\item How many ways can you be dealt at most one face card? [Ans: 11,734,476]
	\item How many ways can you be dealt cards in ascending order of `value', e.g. 6, 7, 8, 9, 10, jack? [Ans: 32,768]
	\end{enumerate}


\end{document}