\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{2: Due 01/29}{All wish to possess knowledge, but few, comparatively speaking, are willing to pay the price.}{Decimus Junius Juvenalis}

% Problem 1
\problem{10} Suppose that the revenue and cost function for a certain item are given by $R(q)= 67.99q$ and $C(q)= 13.47q + 495000$, respectively. 
	\begin{enumerate}[(a)]
	\item How much does the company sell each item for? How much does it cost to make each item?
	\item What are the fixed costs for the production of this good?
	\item What is the profit or loss if the company produces and sells ten-thousand of these items?
	\item What is the break-even point? At least many items does this company need to sell in order to make a profit on this item?
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Leslie owns a wine and spirit store called \textit{Planet of the Grapes}. She rents the building for \$24,730 per month. The average bottle of wine or spirit at her store sells for \$11.56. The average cost of ordering, stocking, and selling these wines/spirits is \$5.21 per bottle. 
	\begin{enumerate}[(a)]
	\item What are the fixed and variable costs for Leslie's business?
	\item Find the cost function for Leslie's business.
	\item Find the revenue function for Leslie's business.
	\item Find the break-even point for Leslie's business. 
	\item What is the minimal average amount of bottles Leslie must sell per month to make a profit?
	\item How many bottles must Leslie sell each month on average to make a profit of \$15,000 (translating to a yearly profit of \$180,000)? Does this seem feasible?	
	\end{enumerate}



\newpage



% Problem 3
\problem{10} Suppose a company produces two items, $q_1$ and $q_2$, and has a cost function given by $C(q_1, q_2)= 7.23 q_1 + 82.56 q_2 + 15721.12$. 
	\begin{enumerate}[(a)]
	\item What are the fixed costs for producing these two items?
	\item What is the total cost associated with producing 30 of the first item and 65 of the second item?
	\item How much does it cost to produce the first item? How much does it cost to produce the second item?
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Suppose that you have a revenue function given by $R(q)= 89q$ and a cost function given by $C(q)= 45q + 7200$. 
	\begin{enumerate}[(a)]
	\item What are the revenue and cost at a production/sale level of 60~units?
	\item Without finding the profit function, find the break-even point for the production/sale of this item.
	\item Find the profit function, $P(q)$.
	\item Compute $P(60)$. Explain how you could use (a) to find $P(60)$. 
	\end{enumerate}


\end{document}