\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{3: Due 09/15}{If people do not believe that mathematics is simple, it is only because they do not realize how complicated life is.}{George Polya}

% Problem 1
\problem{10} Let the universe, $\mathcal{U}$, for $m, n, j, k$ be the set of integers. Define the following predicates:
	\[
	\begin{aligned}
	P(m) &\colon m \text{ is even} \\
	Q(n) &\colon n \text{ is a perfect square} \\
	R(j) &\colon j \text{ is divisible by 3} \\
	S(k) &\colon k \text{ is divisible by 6} \\
	W(\ell) &\colon 1 < \ell \leq 8
	\end{aligned}
	\]
Write the open sentences below as complete English sentences as `simply' as possible and then determine whether the statement is true or false. If the statement is true, explain why. If not, give a counterexample. 
	\begin{enumerate}[(a)]
	\item $(\exists! n) \big( Q(n) \wedge W(n) \big)$ 
	\item $(\forall m) \big( P(m) \vee R(m) \big)$ 
	\item $(\forall m) \big( \neg R(m) \to \neg S(m) \big)$ 
	\item $(\forall m) (\exists n) \big( S(m) \to [(m= 6n) \wedge P(n)] \big)$ 
	\end{enumerate} 



\newpage



% Problem 2
\problem{10} By defining appropriate universes and predicates, quantify the open sentences below. Indicate whether the resulting statement is true or false. No justification is necessary. 
	\begin{enumerate}[(a)]
	\item For all integers $m$, there exists an integer $n$ such that $m= n + 1$.
	\item For all integers $n$, if $n$ is divisible by 5 then the 1's digit of $n$ is either 0 or 5.
	\item Nonzero real numbers have a unique multiplicative inverse. 
	\item Given any pair of distinct integers, there is another integer between them.
	\item Everybody has problems. 
	\end{enumerate}



\newpage



% Problem 3
\problem{10} Being as clear and detailed as possible, explain why $\exists x\, P(x) \wedge \exists x\, Q(x)$ does not imply $\exists x\, [P(x) \wedge Q(x)]$. 



\newpage



% Problem 4
\problem{10} Let $P(x)$ be the predicate $R(x)$: $x$ is a rectangle and let $S(x)$ be the predicate $S(x)$: $x$ is a square. 
	\begin{enumerate}[(a)]
	\item Write $\forall x \big( R(x) \to S(x) \big)$ as a complete English sentence.
	\item Write the contrapositive, converse, and negation of the open sentence in (a) as complete English sentences. 
	\end{enumerate}


\end{document}