\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{7: Due 03/01}{Life is a school of probability.}{Walter Bagehot}

% Problem 1
\problem{10} The probabilities of several events in a finite probability space are given below:
	\[
	\begin{aligned}
	P(A)&= 0.30 & P(B \text{ and } C)&= 0.15 \\
	P(B)&= 0.55 & P(D \;|\; A)&= 0.10 \\
	P(C)&= 0.75 & P(B \text{ and } D)&= 0.01 \\
	P(D)&= 0.25 & P(C \text{ and } D)&= 0.00
	\end{aligned}
	\] 
\begin{enumerate}[(a)]
\item Assuming that $A$ and $B$ are independent, find $P(A \text{ or } B)$.
\item Find $P(C \;|\; B)$.
\item Are $A$ and $C$ disjoint? Explain.
\item Are $B$ and $D$ independent? Explain. 
\item Find $P(A \text{ and } D)$. 
\end{enumerate}



\newpage



% Problem 2
\problem{10} At a small community college, the number of times students accessed tutoring resources available to them during a semester is summarized in the table below. \par
	\begin{table}[!ht]
	\centering
	\begin{tabular}{|l||c|c|c|c|} \hline
	& Never & 1 -- 2 & 3 -- 5 & > 5 \\ \hline \hline
	Freshman & 72 & 86 & 45 & 17 \\ \hline
	Sophomore & 93 & 32 & 55 & 41 \\ \hline
	Junior & 63 & 44 & 46 & 19 \\ \hline
	Senior & 97 & 9 & 15 & 11 \\ \hline
	\end{tabular}
	\end{table} \par
Based on the table above and showing all your work, answer the following:
\begin{enumerate}[(a)]
\item Find the probability that a randomly selected student never went to tutoring.
\item Find the probability that a randomly selected student is a Junior.
\item Find the probability that a randomly selected student went to tutoring once to two times or was a Sophomore. 
\item Find the probability that a randomly selected Senior went to tutoring more than five times. 
\item If a student was a Freshman, find the probability that they went to tutoring at most five times. 
\end{enumerate}



\newpage



% Problem 3
\problem{10} At a local car dealership, there are 460 cars in the lot. Of these cars, 45 of them are electric vehicles and 126 of them are SUVs. There are also 3 which are electric SUVs. 
	\begin{enumerate}[(a)]
	\item Find the probability that a randomly selected car was an electric vehicle. 
	\item Find the probability that a randomly selected car was an electric vehicle or an SUV.
	\item Find the probability that a randomly selected car was neither an electric vehicle nor an SUV.
	\item If a randomly selected car was an SUV, what is the probability that it was electric? 
	\item Find the probability that a randomly selected car was a non-SUV, electric vehicle. 
	\end{enumerate}



\newpage



% Problem 4
\problem{10} You randomly assign delivery trucks routes to make their deliveries around the community. Of these routes, 40\% of them are highways, while the rest of them are surface streets. If a delivery truck takes the highway, they make their deliveries on-time 90\% of the time. If a delivery truck takes surface streets, they make their delivery on-time 85\% of the time.
	\begin{enumerate}[(a)]
	\item What percent of deliveries are on-time?
	\item What percent of deliveries are on-time or use surface streets?
	\item What percent of deliveries use highways?
	\item What percent of deliveries that use the highway are on-time?
	\item What percent of deliveries that are on-time use the highway?
	\end{enumerate}


\end{document}