\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{13: Due 11/10}{\dots there is no apparent reason why one number is prime and another not. To the contrary, upon looking at these numbers one has the feeling of being in the presence of one of the inexplicable secrets of creation.}{Don Zagier}

% Problem 1
\problem{10} Showing all your work and fully justifying your reasoning, complete the following:
	\begin{enumerate}[(a)]
	\item Using the definition of even, show that $-484$ is even.
	\item Using the definition of odd, show that 151 is odd.
	\item Find the prime factorization of 360. 
	\item Find all the prime divisors of 45!. 
	\item Can an integer of the form $n^4 - 9$, where $n \in \mathbb{Z}$, be prime?
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Showing all your work and fully justifying your reasoning, complete the following:
	\begin{enumerate}[(a)]
	\item List at least ten multiples of 17.
	\item List the divisors of 120.
	\item What are the prime divisors of 120?
	\end{enumerate}



\newpage



% Problem 3
\problem{10} Showing all your work and justifying your reasoning, complete the following:
	\begin{enumerate}[(a)]
	\item By enumerating the divisors of 40 and 100, compute $\gcd(40, 100)$.
	\item By enumerating sufficient multiples of 25 and 60, compute $\lcm(25, 60)$.
	\item Compute $\gcd(2^{100} \cdot 3^{200} \cdot 5^{600} \cdot 11^{100},\, 2^{300} \cdot 3^{100} \cdot 5^{600} \cdot 7^{800})$. 
	\item Compute $\lcm(2^{100} \cdot 3^{200} \cdot 5^{600} \cdot 11^{100},\, 2^{300} \cdot 3^{100} \cdot 5^{600} \cdot 7^{800})$. 
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Showing all your work and justifying your reasoning, complete the following:
	\begin{enumerate}[(a)]
	\item Prove or disprove: if $p$ is prime, then $p^2 + 1$ is also prime. 
	\item Using the fact that $ab= \lcm(a, b) \cdot \gcd(a, b)$ and $\gcd(196, 1320)= 4$, compute $\lcm(196, 1320)$. 
	\item If $a, b \in \mathbb{Z}$ such that $\gcd(a, b)= p$, where $p$ is prime, what are the possible values for $\gcd(a^2, b)$, $\gcd(a, b^2)$, $\gcd(a^2, b^2)$, and $\gcd(a^2, b^3)$? 
	\end{enumerate}


\end{document}