\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{10: Due 11/16}{If you rearrange the letters of Peru, you could spell Europe.}{Andy Dwyer, Parks and Recreation}

% Problem 1
\problem{10} Dr. Anne Graham runs a clinic in her hometown. To be prepared for variations in tax rates, she sets aside \$800 per month from the business' profits into an account that earns 3.2\% yearly interest, compounded quarterly. 
\begin{enumerate}[(a)]
\item Assuming the money has not been used, how much is in the account after 3~years?
\item If she wants to be prepared for a sudden \$10,000 increase in yearly taxes, how much should she be setting aside each month from the business' profits? [Assume the account will start with \$0.]
\end{enumerate}





\newpage





% Problem 2
\problem{10} Rebecca Law and her husband Marshall are saving money for their first child's college fund. They are going to make three yearly payments, equally spaced, into a savings account that earns 2.8\% interest, compounded annually. 
\begin{enumerate}[(a)]
\item If they want to have \$30,000 saved by the time their newborn turns 18, what should these payments be?
\item How long until the account has \$20,000?
\end{enumerate}





\newpage





% Problem 3
\problem{10} Richard O'Shea has a credit card with \$4,800 already on the card. Suppose the yearly interest rate on the card is 18.24\%, compounded monthly. 
\begin{enumerate}[(a)]
\item Suppose the credit card company computes the monthly minimum payment by supposing that you are going to pay off the amount in even amounts over 10~years. How is Rick's current monthly minimum payment?
\item If Rick did not spend any additional money and paid off the credit card in 10~years, how much interest would he have paid assuming he paid the fixed monthly minimum from (a).
\item Suppose the monthly minimum was fixed, after 18~months, how much of the monthly minimum payment is going towards the debt remaining and how much is being used to pay interest?
\item Rick plans on paying off the card sooner than by using the monthly minimums. If he wants to pay the card off in 2~years, how much should he be paying per month?
\end{enumerate}





\newpage





% Problem 4
\problem{10} Kurt C. Hose and his wife Gutta bought a home for \$86,000 that is amortized over 25~years, after a 15\% down payment. The interest on the house is 13\%, compounded monthly. 
\begin{enumerate}
\item What are the monthly mortgage payments?
\item How much has been paid to date after 10~years?
\item How much of the loan remains to be paid after 10~years?
\end{enumerate}

\end{document}