\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{3: Due 09/19}{Money is not the most important thing in the world. Love is. Fortunately, I love money.}{Jackie Mason}

% Problem 1
\problem{10} The CPI in 2022 was approximately 296.071. According the the US Bureau of Labor Statistics, the current CPI is 307.026.
	\begin{enumerate}[(a)]
	\item Find the inflation rate from 2022 to 2023. 
	\item If the inflation rate in (a) continues from 2023 to 2024, estimate the cost of a good next year that costs \$46.99 this year,
	\item If the inflation rate in (a) remains constant across the next year, what will the increase in prices be from 2023 to 2028? 
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Stevie runs a shop that sells hot teas and baked beans. The shop is, surprisingly, not doing well. She decides to take out a simple discount note to pay for some additional advertising in the hopes that it will drive customers to the store. The note the bank offers is \$8,000 for 7~months at 8.3\% annual interest.
	\begin{enumerate}[(a)]
	\item What is the maturity for this simple discount note?
	\item What is the discount for this note?
	\item What is the interest Stevie pays on this loan?
	\item How much does Stevie receive from the bank?
	\item At the end of the 7~months, how much does Stevie owe the bank?
	\end{enumerate}


\end{document}