\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{7: Due 10/02}{If we hit that bullseye, the rest of the dominoes should fall like a house of cards. Checkmate.}{Zapp Brannigan, Futurama}

% Problem 1
\problem{10} Express the following decimal numbers in scientific notation:
	\begin{enumerate}[(a)]
	\item $5$
	\item $10.3$
	\item $0.000000123$
	\item $159000000$
	\item $0.4$
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Express the following numbers in scientific notation as decimal numbers:
	\begin{enumerate}[(a)]
	\item $5.23 \cdot 10^5$
	\item $1.3 \cdot 10^0$
	\item $9.7 \cdot 10^{-8}$
	\item $4.0 \cdot 10^3$
	\item $5.782 \cdot 10^{10}$
	\end{enumerate}



\newpage



% Problem 3
\problem{10} Showing all your work and expressing the result in scientific notation with three significant figures, convert the following:
	\begin{enumerate}[(a)]
	\item 0.008 megagrams to centigrams
	\item 120~oz to stones [1~oz = 28.35~g, 1~stone = 6.35~kg]
	\item 3~gallons to milliliters [1~gal = 3.785~L]
	\item 2.16 $\cdot$ 10$^9$~ft$^3$ to mi$^3$ [5,280~ft = 1~mi.]
	\item 3.72 meters per square second to feet per square minute [0.3048~m = 1~ft]
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Suppose you are talking with your friend who has moved to Italy. The conversation has drifted to Miami housing. Currently, the cost of space in Miami is approximately \$464 per square foot. 
	\begin{enumerate}[(a)]
	\item For your friend, convert this to Euros per square meter. [\texteuro 1= \$1.07; 1~ft = 0.3048~m]
	\item Using (a), find the conversion factor from dollars per square foot to Euros per square meter. 
	\item Use your answer from (b) to convert \$1,845 per square foot to Euros per square meter. 
	\end{enumerate}


\end{document}