\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{9: Due 04/11}{Economics has never been a science---and it is even less now than a few years ago.}{Paul A. Samuelson}

% Problem 1
\problem{10} Bennie Factor is setting up a college fund for his children. He will deposit \$1,500 every 6~months into an account that earns 4.6\% annual interest, compounded semiannually. How much is in the account after 18~years?



\newpage



% Problem 2
\problem{10} Holly Wood is saving money for her senior project in film school. To produce her film, she needs \$6,000 in 18~months. If she makes equal monthly payments into an account earning 2.3\% annual interest, compounded monthly, how much money does she need to deposit into the account each month?



\newpage



% Problem 3
\problem{10} Jack Pott wins a \$125,000 lottery. To make the money last as long as possible, he deposits this money into an account that earns 8\% annual interest, compounded quarterly. If he wants to withdraw money from this account monthly so that the money lasts 10~years, what should he withdraw from the account each month?



\newpage



% Problem 4
\problem{10} To purchase a new car, Horace Cope takes out a loan for \$9,000 at a rate of 8.5\% annual interest, compounded monthly. He will make equal monthly payments on this loan for 2~years. What are the monthly payments?


\end{document}