\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{11: Due 11/01}{There are three types of lies: lies, damn lies, and statistics.}{Benjamin Disraeli}

% Problem 1
\problem{10} Suppose Kevin and Cristine work at a company where the salaries are normally distributed. Kevin's salary corresponds to a $z$-score of $z_K= -0.47$ and Cristine's salary corresponds to a $z$-score of $z_C= 1.62$. 
	\begin{enumerate}[(a)]
	\item Who makes less money? Explain.
	\item What percent of workers at the company many less than Cristine? Explain.
	\item What percent of workers at the company make more than Kevin? Explain.
	\item If the salary have distribution $N(\$68327, \$7419)$, find the amount Kevin and Cristine make. 
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Suppose Bill wants to purchase a house. Based on his salary, the most expensive house he can afford is \$380,000. Looking up housing data for his county on a government website, he finds that the local housing prices indicate that the housing costs are approximately normally distributed with the average house cost approximately \$450,000 and standard deviation \$52,000. What percent of houses in his area can Bill afford? 



\newpage



% Problem 3
\problem{10} A highly desired university receives more applicants than they could ever hope to accept. In fact, they receive so many applications, it is overly burdensome to thoroughly examine each application. They are only able to screen approximately 45\% of the applications that they receive. To reduce the number of applications, they will not screen applicants that receive below a certain score on an entrance exam. The entrance exam is known to have scores that are normally distributed with mean 340 and standard deviation 32. What is the minimum score you can receive to have this school actually screen your application? 


\end{document}