\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{5: Due 01/06}{

% Problem 1
\problem{10} Showing all of your work, compute the following:
	\begin{enumerate}[(a)]
	\item 87\% of 19120
	\item 45\% of 760
	\item 3\% of 49
	\item 170\% of 160
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Showing all of your work, compute the following:
	\begin{enumerate}[(a)]
	\item 560 increased by 35\%
	\item 49 decreased by 25\%
	\item 1890 increased by 140\%
	\item 650 decreased by 98\%
	\end{enumerate}



\newpage



% Problem 3
\problem{10} Consider the product $345(1.42)$.
	\begin{enumerate}[(a)]
	\item Compute this product. 
	\item Interpret your answer in (a) as finding a certain percentage of a certain number. 
	\item Interpret your answer in (a) as finding a percentage increase or decrease of a certain number. 
	\end{enumerate}



\newpage



% Problem 4
\problem{10} You are looking at purchasing a certain product. You may buy an older model of this product for \$19,299. There is a newer model for \$22,780 that is on sale for 15\% off. 
	\begin{enumerate}[(a)]
	\item Find the discount on the second product.
	\item Find the sale price on the second product. 
	\item Which product is a ``better deal''? Explain. 
	\end{enumerate}



\newpage



% Problem 5
\problem{10} Suppose the CPI last year was \$320.41. This year the CPI was \$337.61.
	\begin{enumerate}[(a)]
	\item Find the inflation rate from last year to this year. 
	\item Estimate how much a product that cost \$79.99 last year would cost this year.
	\item If this inflation rate continues for the next 6~years, what will be the inflation rate from this year to that year? 
	\end{enumerate}


\end{document}