\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{17: Due 12/06}{Some mathematicians feel that combinatorial analysis is not a branch of mathematics but rather a collection of clever but unrelated tricks.}{Frank Harary}

% Problem 1
\problem{10} Suppose there are 8 appetizers, 15 entr\'ees, and 6 desserts available at a restaurant. Using the multiplication principle or the addition principle, answer the following: 
	\begin{enumerate}[(a)]
	\item How many ways can you order either an appetizer, entr\'ees, or dessert? [Ans: 29]
	\item How many ways can you order a meal, i.e. appetizer, entr\'ees, and dessert. [Ans: 720]
	\item How many ways can you order either an appetizer and an entr\'ee, or an appetizer and a dessert? [Ans: 168]
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Using the theory of permutations, showing all your work, and fully justifying your reasoning, compute the following:
	\begin{enumerate}[(a)]
	\item The number of possible ways 15 people can finish a race, assuming that ties are not possible. [Ans: 1,307,674,368,000]
	\item The number of possible president, vice president, secretary, and treasurer that can be elected from 486 people, assuming no individual can hold more than one role. [Ans: 55,102,398,120]
	\item The number of possible passwords using 12~characters, assuming a character can be a digit or uppercase/lowercase letter. [Ans: 3,226,266,762,397,899,821,056]
	\item The number of distinct possible arrangements of the letters of the word `syzygy.' [Ans: 120]
	\end{enumerate}



\newpage



% Problem 3
\problem{10} Using the theory of combinations, showing all your work, and fully justifying your reasoning, compute the following:	
	\begin{enumerate}[(a)]
	\item How many ways are there to choose a committee of 6 people from a collection of 20 people? [Ans: 38,760]
	\item How many 6 card hands can be dealt from a deck of 52 cards? [Ans: 20,358,520]
	\item How many ways are there to select any four bills from a jar containing a large number of \$1, \$5, \$10, \$20, \$50, and \$100 bills? [Ans: 70]
	\item How many nonnegative solutions $(x_1, x_2, x_3, x_4, x_5)$ are there to the equation $x_1 + x_2 + x_3 + x_4 + x_5= 100$? [Ans: 4,598,126]
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Showing all your work and fully justifying your reasoning, answer the following:
	\begin{enumerate}[(a)]
	\item How many ways can the word `frustrating' be arranged so that there are 4~letters between the `u`' and `g'? [Ans: 1,088,640]
	\item How many ways can you choose a committee of 10 people with a designated representative for the committee from a collection of 50 people? [Ans: 102,722,781,700]
	\item If 50 people are broken up into groups by assigning to them to 4 rooms with 35 seats each, does one of the rooms have to have at least 13 people? Does one of the rooms have to have at least 23 empty seats?
	\item If you have a jury pool consisting of 14 men and 16 women, how many juries can be formed consisting of 5 men and 7 women? [Ans: 22,902,880]
	\end{enumerate}

\end{document}