\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

\newcommand{\blank}[1]{\underline{\hspace{#1}}} % Blank Underline

% -------------------
% Content
% -------------------
\begin{document}

\homework{12: Due 11/10}{No part of mathematics is ever, in the long run, ``useless.'' Most of number theory has very few ``practical'' applications. That does not reduce its importance, and if anything it enhances its fascination. No one can predict when what seems to be a most obscure theorem may suddenly be called upon to play some vital and hitherto unsuspected role.}{C. Stanley}

% Problem 1
\problem{10} Showing all your work and fully justifying your answer, complete the following:
	\begin{enumerate}[(a)]
	\item From the definition, determine whether 79 is odd or even. 
	\item From the definition, determine whether or not $-343$ a perfect cube.
	\item Find the prime factorization of 840. Find all the divisors of 840. 
	\item Can an integer of the form $n^2 + 7n + 6$, where $n \in \mathbb{N}$, be prime? Explain. 
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Using the given $a, b$, express the division $\frac{b}{a}$ using the division algorithm. Be sure to show all your work. 
	\begin{enumerate}[(a)]
	\item $a= 16$, $b= 2797$
	\item $a= -29$, $b= -7015$
	\item $a= 56$, $b= 55664$
	\end{enumerate}



\newpage



% Problem 3
\problem{10} Showing all your work and fully justifying your reasoning, complete the following: 
	\begin{enumerate}[(a)]
	\item Use the Euclidean Algorithm to find $\gcd(459, 303)$. 
	\item Use the extended Euclidean algorithm, express $\gcd(459, 303)$ as a linear combination of 459 and 303. 
	\item Is it possible to find integers $x, y$ such that $459x + 301y= 5$? If not, explain why. If so, find them.  
	\item Is it possible to find integers $x, y$ such that $459x + 301y= 6$? If not, explain why. If so, find them.  
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Showing all your work, convert the given base-10 number, binary number, or hexadecimal to the given base $b$:
	\begin{enumerate}[(a)]
	\item $7187$; $b= 16$
	\item $119$; $b= 2$
	\item $11101_2$; $b= 10$
	\item $801\text{c}$; $b= 10$
	\end{enumerate}


\end{document}