\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{14: Due 11/07}{So much of life, it seems to me, is determined by pure randomness.}{Sidney Poitier}

% Problem 1
\problem{10} Previous surveys indicate that that a mere 15\% of the voting population in a state support the governor. Suppose you take a simple random sample of 19~voters.
	\begin{enumerate}[(a)]
	\item What is the probability that none of them support the governor?
	\item What is the probability that less than five of them support the governor?
	\item What is the probability that five or more of them support the governor?
	\item If instead you took a survey of 1,200 voters. What is the probability that more than 17\% of them support the governor?
	\end{enumerate}



\newpage



% Problem 2
\problem{10} A think tank is testing support for a new increase in tax to support local road improvements. Previous tax increases had 45\% of the population in support of the bill. Suppose support has not changed since then. The think tank performs a survey of 300~individuals. 
	\begin{enumerate}[(a)]
	\item Find the probability that less than 120~people surveyed support the new tax.
	\item Find the probability that more than 155~people surveyed support the new tax.
	\item Find the probability that between 120 and 155~people surveyed support the new tax.
	\item Use the continuity correction to improve the estimation of the probability in (a).
	\end{enumerate}


\end{document}