\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{3: Due 09/26}{I'm never going to financially recover from this.}{Joe Exotic, Tiger King}

% Problem 1
\problem{10} Write the following decimal numbers in scientific notation:
	\begin{enumerate}[(a)]
	\item 1\,541\,000
	\item 40\,000
	\item 0.6
	\item 4
	\item 0.00000008
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Write the following numbers in scientific notation as decimal numbers:
	\begin{enumerate}[(a)]
	\item $5.2 \cdot 10^0$
	\item $1.7 \cdot 10^5$
	\item $6.4 \cdot 10^{-1}$
	\item $9.1 \cdot 10^{-5}$
	\item $7.6 \cdot 10^1$
	\end{enumerate}



\newpage



% Problem 3
\problem{10} Showing all your work, compute the following:
	\begin{enumerate}[(a)]
	\item 46\% of 1320
	\item 90\% of 40
	\item 39.6\% of 8476
	\item 1\% of 19.5
	\item 265\% of 210
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Showing all your work, compute the following:
	\begin{enumerate}[(a)]
	\item 750 increased by 15\%
	\item 60 decreased by 33\%
	\item 840 increased by 92\%
	\item 431 decreased by 99\%
	\item 15 increased by 170\%
	\end{enumerate}

	

\newpage



% Problem 5
\problem{10} A laptop from Macrosoft is advertised as being \$999. You plan on ordering this computer online. You know that you will be charged 7\% sales tax. How much will the computer then cost? If you find out that the laptop costs Macrosoft \$89 to produce, what is the percent markup that Macrosoft puts on this laptop? How much profit do they make per laptop? 



\newpage



% Problem 6
\problem{10} Jeff is arguing with Carol. Over the last 7~months, the cost of products has risen 4\% each month. Jeff then argues that goods now cost $7 \cdot 4\%= 28\%$ more now than they cost 4~months ago. Carol claims that this is not correct and that goods now cost a little more than 30\% more than they did 7~months ago. Who is correct? Be sure to fully justify your response. 


\end{document}