\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{13: Due 03/25}{That's the thing. I don't think I believe in deep down. I kinda think that all you are is just the things that you do.}{Diane Nguyen, BoJack Horseman}

% Problem 1
\problem{10} Psychologists are examining how students cope with failure. They find estimates that 20\% of individuals will fail at least one course during their lifetime. Suppose that you take a simple random sample of nine students. 
	\begin{enumerate}[(a)]
	\item What is the probability that exactly 4 of them have failed a course?
	\item What is the probability that at least one of them has failed a course?
	\item What is the probability that less than 5 of them failed a course? 
	\item What is the probability that exactly 8 of them failed a course?
	\end{enumerate}



\newpage



% Problem 2
\problem{10} A state senate race has grown increasing tense as scandal has struck the incumbents office, resulting a huge drop in their support. It is currently estimated that only 10\% of voters currently support the incumbent. Suppose pollsters take a simple random sample of 15 potential voters. 
	\begin{enumerate}[(a)]
	\item What is the probability that more than 8 of them support the incumbent? 
	\item What is the probability that less than 4 of them support the incumbent? 
	\item What is the probability that at least one of them support the incumbent?
	\end{enumerate}


\end{document}