\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{1: Due 09/11}{I'm fine. It's just that life is pointless and nothing matters and I'm always tired.}{Andy Dwyer, Parks and Recreation}

% Problem 1
\problem{10} Complete the following:
	\begin{enumerate}[(a)]
	\item List all the divisors of 80.
	\item List all the nonnegative multiples of 15 less than 180. 
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Showing all your work, find the prime factorizations of the following:
	\begin{enumerate}[(a)]
	\item $40$
	\item $90$
	\item $97$
	\item $99$
	\item $228$
	\end{enumerate}



\newpage



% Problem 3
\problem{10} Without using a calculator, answer the following:
	\begin{enumerate}[(a)]
	\item Does 2 divide 8455? Explain.
	\item Does 3 divide 19436? Explain.
	\item Does 4 divide 764136? Explain.
	\item Does 5 divide 99999? Explain.
	\item Does 9 divide 331443? Explain. 
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Complete the following:
	\begin{enumerate}[(a)]
	\item List all the prime numbers up to 34.
	\item Compute $\sqrt{1223}$.
	\item Using (a) and (b), explain why 1223 is a prime number. 
	\end{enumerate}



\newpage



% Problem 5
\problem{10} Showing all your work, compute the following:
	\begin{enumerate}[(a)]
	\item $\gcd(15, 33)$
	\item $\lcm(15, 33)$
	\item $\gcd(2^{70} \cdot 3^{40} \cdot 7^{60} \cdot 11^{20},\, 2^{90} \cdot 5^{48} \cdot 7^{50} \cdot 11^{20})$
	\item $\lcm(2^{70} \cdot 3^{40} \cdot 7^{60} \cdot 11^{20},\, 2^{90} \cdot 5^{48} \cdot 7^{50} \cdot 11^{20})$
	\end{enumerate} 



\newpage



% Problem 6
\problem{10} Isabella has two large wood strips. One is 70~ft long and the other is 98~ft long. She needs to cut them down into boards. The size of the boards does not matter, so long as they are all of equal size. She has a `template' that will let her cut the wood to specific integer lengths, but it must be reset if you change the length---which is time consuming. To what length should she set the template in order to never have to reset it and cut each strip into pieces of equal length? 


\end{document}