\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{9: Due 10/24}{I like to play blackjack. I'm not addicted to gambling. I'm addicted to sitting in a semicircle.}{Mitch Hedberg}

% Problem 1
\problem{10} Suppose you play a game where you roll a loaded die. The probabilities for this die are (partially) given below. If you roll an even number, you win \$1. If you roll a one, you lose \$5. If you roll a three, you lose \$2. Finally, if you roll a five, you win/lose nothing. 
	\begin{table}[!ht]
	\centering 
	\begin{tabular}{|c||c|c|c|c|c|c|} \hline 
	$n$ & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ \\ \hline 
	$P(n)$ & $\phantom{\dfrac{00}{00}}$ & $\dfrac{2}{12}$ & $\dfrac{3}{12}$ & $\dfrac{1}{12}$ & $\dfrac{1}{12}$ & $\dfrac{4\rule{0pt}{2.9ex}}{12\rule[-1.3ex]{0pt}{0pt}}$ \\ \hline
	\end{tabular}
	\end{table}

\begin{enumerate}[(a)]
\item Find $P(1)$. 
\item Find the probability that if you roll the die three times, you win \$1 each time. 
\item Find the average amount you win per game. 
\item Should you play this game? Explain.
\end{enumerate}



\newpage



% Problem 2
\problem{10} Suppose you are designing a game to `reallocate' money from your friends to an account that you control\dots You will have them roll a four-sided dice---each side equally likely to occur. If they roll a four, neither of you wins money. If they roll a two or three, you will pay them \$2 or \$3, respectively. If they roll a one, they will flip a fair coin. If the coin is heads, they win/lose nothing. However, if the coins is tails, they will pay you some amount of money. 
	\begin{enumerate}[(a)]
	\item Find the amount your friend must pay you if they roll a one and then flip a tails so that you will not lose money at this game `in the long run.' 
	\item If your friend plays this game one-hundred times, are you guaranteed to make money? Explain. 
	\end{enumerate}


\end{document}