\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,bmargin=1in,tmargin=1in]{geometry}
\usepackage{style}

\pagenumbering{gobble}


% -------------------
% Content
% -------------------
\begin{document}

% TItle
\begin{center} 
\bfseries
\color{stacred}
\LARGE Syllabus Quick Facts \par\vspace{0.2\baselineskip}
\Large MATH 104: Pre-Calculus Mathematics --- Spring 2023
\end{center} \pspace


% Course Information
\mysection{0.27}{Course Information}
\hspace{0.53cm} {\itshape Instructor Email}: \href{mailto:cmcwhort@stac.edu}{cmcwhort@stac.edu} \par
\hspace{0.53cm} {\itshape Course Webpage}: \href{https://coffeeintotheorems.com/courses/2023-2/spring/math-104/}{https://coffeeintotheorems.com/courses/2023-2/spring/math-104/} \par
\hspace{0.53cm} {\itshape Office Hours}: 	\par \vspace{-0.3cm}
	\begin{table}[!ht]
	\centering
	\begin{tabular}{l || l}
	Mon. & 11:30~am -- 12:30~pm \\
	Tues. & 1:00~pm -- 2:00~pm \\
	Wed. & 11:30~am -- 12:30~pm \\
	Thurs. & 1:00~pm -- 2:00~pm \\
	Fri. & 11:30~am -- 1:30~pm
	\end{tabular}
	\end{table} \pspace


% Grading Components
\mysection{0.27}{Grading Components}
Course grades are determined by the following components: \par \vspace{-0.3cm}
	\begin{table}[!ht]
        \begin{tabular}{clr}
	& Quizzes & 15\% \\
	& Homework (Written) & 15\% \\
	& Homework (Online) & 25\% \\
	& Exams & 45\%
        \end{tabular} 
        \end{table}


% Attendance 
\mysection{0.27}{Attendance}
Attend each lecture and show up on time. Anticipated absences should be addressed with the instructor in advance of the absence. Address any absences---anticipated or otherwise---with the instructor. If you miss a lecture, you are responsible for any material covered, any work assigned, any course changes made, etc. during the class. Four or more unexcused absences from lectures could result in receiving a grade penalty per additional absence or an `F' in the course. Furthermore, excessive lateness will also count as an absence. \pspace


% Quizzes 
\mysection{0.27}{Quizzes}
There will be a quiz \textit{every} class, typically at the start of class. Because solutions will often then be immediately discussed, no make-up quizzes will be given (except under extraordinary circumstances). \pspace


% Homework
\mysection{0.18}{Homework\label{hw}}
Homeworks are essential for learning course material and will be what you spend most of your outside time doing. Extensions on these homeworks may be possible. However, requests for extensions should be made at least 24-hours in advance, if at all possible. Any extensions, due dates, and grade penalties for late assignments will be determined by the instructor on a student-by-student basis. There are two homework components: written homework and online homework. 



\newpage



{\itshape\bfseries\color{stacred}Written Homework.} Written homework will occur less often than online homework. The purpose of these homeworks is to give feedback on written solutions. Therefore, these will focus on the most important, difficult, or confusing course topics. In addition, these homeworks will often be shorter. Because of these two factors, students should put special effort into producing their best work---including full solutions with written explanations and all necessary work shown. Students should treat these homework problems as if they were exam problems. This way, you will receive feedback on how you would perform on similar problems during an exam. Be sure to start these homeworks early and as your instructor for help if you are experience difficulties! \pspace

{\itshape\bfseries\color{stacred}Online Homework.} The majority of course homework will be done using an online homework system through the Macmillan `Achieve' learning system. Be sure to regularly check the Achieve system---at least daily---to be sure that you are keeping up with assignments. You will enroll in the course using the Macmillan website. First, create an account (if you do not already have one) using the following link: \href{https://store.macmillanlearning.com/us/login}{https://store.macmillanlearning.com/us/login}. You then add the course using the following course code: \texttt{y487tf}. The Achieve system will allow you to access not only the assignments, additional materials, but a digital copy of the textbook. \pspace


% Exams
\mysection{0.18}{Exams\label{exams}}
There will be three exams in this course, each worth 15\% of the total course grade for a total of 45\% of the course grade. The tentative schedule for these exams can be found below. Each exam covers course material, up until the exam preceding it. While the exams are not cumulative, topics from previous exams can appear in an exam if the material is relevant---but it will not be the focus of the exam. You should be present, seated, and prepared for a scheduled exam before the exam begins. If you are late, you should not expect extra exam time. There are no make-up exams except under extraordinary circumstances. \pspace


% Course Schedule 
\mysection{0.27}{Course Schedule}
The following is a \emph{tentative} schedule for the course and is subject to change. 
        \begin{table}[!ht]
        \centering
        \scalebox{1}{%
        \begin{tabular}{ll || ll}
        Date & Topic(s) & Date & Topic(s) \\ \hline 
	01/24 & Review, \S P1 -- \S P3 & 03/16 & Spring Break \\
	01/26 & Functions, \S1.1, 2.1 & 03/21 & Trigonometry, \S8.1 \\
	01/31 & Functions, \S2.3, 2.2 & 03/23 & Trigonometry, \S8.2, 8.3 \\
	02/02 & Linear Functions, \S3.1 & 03/28 & Trigonometry, \S9.1, 9.2 \\
	02/07 & Exponential Functions, \S3.2, 3.3 & 03/30 & Trigonometry, \S8.5 \\
	02/09 & Review & 04/04 & Review \\
	02/14 & Logarithmic Functions, \S4.1, 4.2 & 04/06 & Exam 2 \\
	02/16 & Logarithmic Functions, \S4.3 & 04/11 & Calculus Prep, \S1.2 -- 1.4 \\
	02/21 & Review & 04/13 & Polynomial \& Rational Functions, \S5.1, 5.2 \\
	02/23 & Exam 1 & 04/18 & Polynomial \& Rational Functions, \S5.3, 5.4 \\
	02/28 & Trigonometry, \S6.1/7.1, 6.2/7.2 & 04/20 & Polynomial \& Rational Functions, \S5.5 \\
	03/02 & Trigonometry, \S6.3/7.3, 6.4/7.4 & 04/25 & Calculus Prep. \\
	03/07 & Trigonometry, \S7.1, 7.2 & 04/27 & Calculus Prep. \\
	03/09 & Trigonometry, \S8.4 & 05/02 & Review \\
	03/14 & Spring Break & 05/04 & Exam 3
        \end{tabular}
        }
        \end{table}


\end{document}