\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{2: Due 09/13}{I wasn't a failed DJ. I was pre-successful.}{Jason Mendoza, The Good Place}

% Problem 1
\problem{10} Your history class course grade is determined by the following components: \par
	\begin{table}[h]
	\centering
	\begin{tabular}{lr}
	Homeworks & 25\% \\
	Paper I & 10\% \\
	Paper II & 10\% \\
	Paper III & 10\% \\
	Project & 30\% \\
	Quizzes & 15\%
	\end{tabular}
	\end{table} \par
Suppose that your homework average was 82\%, your grades on the papers were 68\%, 84\%, and 76\%, respectively, your project grade was 88\%, and your quiz average was 94\%. 
	\begin{enumerate}[(a)]
	\item Compute your course average.
	\item If the project was a final project that had not yet occurred, i.e. you had not yet received the 88\%, but all the other course grades were as listed above, then what is your current course average?
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Suppose you received the following grades this semester: \par
	\begin{table}[h]
	\centering
	\begin{tabular}{lrc}
	Course & Credits & Grade \\ \hline
	BIO 101: Human Biology & 3 & B \\
	MATH 104: Precalculus & 4 & B+ \\
	RELS 102: Religion and Society & 3 & A-- \\
	ENG 207: Writing about World Mythology & 3 & B-- \\
	ECON 102: Principles of Microeconomics & 3 & C+
	\end{tabular}
	\end{table} \par
Given the following grade weights, 
	\begin{table}[h]
	\centering
	\begin{tabular}{lrclr}
	Grade & Weight & & Grade & Weight \\ \hline
	A & 4.0 & \hspace{1cm} & C+ & 2.3 \\
	A-- & 3.7 & & C & 2.0 \\
	B+ & 3.3 & & C-- & 1.7 \\
	B & 3.0 & & D & 1.0 \\
	B-- & 2.7 & & F & 0
	\end{tabular}
	\end{table}

\begin{enumerate}[(a)]
\item Compute your semester GPA. 
\item If your previous GPA based on 67 credits was 3.308, what is your current overall GPA?
\end{enumerate}



\newpage



% Problem 3
\problem{10} Showing all your work, convert the following:
	\begin{enumerate}[(a)]
	\item 0.4 megagrams to centigrams
	\item 87~oz to stones [1~oz = 28.35~g, 1~stone = 6.35~kg]
	\item \$98 per hour to MXP per minute [\$0.057 = 1 MXP]
	\item 6,000~ft$^2$ to mi$^2$ [5280~ft = 1~mi.]
	\item 0.05 meters per square second to feet per square hour
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Suppose you are talking with your friend who has moved to Germany. The conversation has drifted to NYC housing. Currently, the cost of space in NYC is approximately \$1,600 per square foot. 
	\begin{enumerate}[(a)]
	\item For your friend, convert this to Euros per square meter. [\texteuro 1= \$1.07; 1~ft = 0.3048~m]
	\item Using (a), find the conversion factor from dollars per square foot to Euros per square meter. 
	\item Use your answer from (b) to convert \$1,845 per square foot to Euros per square meter. 
	\end{enumerate}


\end{document}