\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{20: Due 12/05}{The only normal people are the ones you don't know very well.}{Alfred Adler}

% Problem 1
\problem{10} Given the binomial distributions below, find the probability of the event(s) indicated. 
	\begin{enumerate}[(a)]
	\item $B(0.40, 7)$, $P(X= 4)$
	\item $B(0.25, 12)$, $P(X < 3)$
	\item $B(0.50, 4)$, $P(X \geq 1)$
	\item $B(0.10, 15)$, $P(X > 5)$
	\item $B(0.15, 8)$, $P(2 < X \leq 6)$
	\end{enumerate}


\newpage


% Problem 2
\problem{10} Suppose at a school that 15\% of students do not receive any scholarships. If you take a simple random sample of 14 students, find the probability that\dots
	\begin{enumerate}[(a)]
	\item exactly four of the students did not receive any scholarships. 
	\item five or more of the students did not receive any scholarships.
	\item at least one of the students did not receive any scholarships.
	\item less than 3 of the students did not receive any scholarships.
	\item none of the students received a scholarship. 
	\end{enumerate}



\newpage



% Problem 3
\problem{10} A city is considering whether or not to build a park in a newly acquired lot. It is estimated that 53\% of the population is in favor of building the park. The city conducts a survey of its residents consisting of 300 people. What is the approximate probability that between 140 and 170 people surveyed are in favor of the park?


\end{document}