\documentclass[12pt,letterpaper]{exam}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/exams}

% -------------------
% Course & Exam Information
% -------------------
\newcommand{\course}{MAT 104: Exam 3}
\newcommand{\term}{Spring -- 2023}
\newcommand{\examdate}{05/04/2023}
\newcommand{\timelimit}{85 Minutes}

\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\examtitle
\instructions{Write your name on the appropriate line on the exam cover sheet. This exam contains \numpages\ pages (including this cover page) and \numquestions\ questions. Check that you have every page of the exam. Answer the questions in the spaces provided on the question sheets. Be sure to answer every part of each question and show all your work.} 
\scores
%\bottomline
\newpage

% ---------
% Questions
% ---------
\begin{questions}


% Question 1
\newpage
\question[10] Find the average rate of the function $f(x)= \dfrac{x + 1}{x - 3}$ on the interval $[-1, 4]$. 



% Question 2
\newpage
\question[10] Find the average rate of change of the function $f(x)= x^2 + x - 3$ on the interval $[a, a + h]$. 



% Question 3
\newpage
\question[10] Factor the polynomial $x^3 + 3x^2 - 28x$ as completely as possible. 



% Question 4
\newpage
\question[10] Factor the polynomial $2x^2 - 6x - 36$ as completely as possible. 



% Question 5
\newpage
\question[10] Factor the polynomial $(16x^4 - 1)(x + 4) + (16x^4 - 1)(x - 3)$ as completely as possible. 



% Question 6
\newpage
\question[10] Use the quadratic formula to factor the polynomial $24x^2 + 77x + 60$. 



% Question 7
\newpage
\question[10] Use the discriminant to explain why the polynomial $x^2 - 10x + 7$ does not factor over the integers. Use the quadratic formula to factor the polynomial. 



% Question 8
\newpage
\question[10] A polynomial, $p(x)$, of degree two has roots $x= -6$ and $x= 5$. Furthermore, the polynomial $p(x)$ is such that $p(4)= -30$. Find the polynomial $p(x)$. 



% Question 9
\newpage
\question[10] List all the possible rational roots for the polynomial $3x^5 + 8x^4 - 7x^2 + 9x - 6$. 



% Question 10 
\newpage
\question[10] Find the quotient and remainder when $x^5 + 3x^4 + 2x^3 + 4x^2 - 30x + 13$ is divided by $x^2 + 3x - 2$. 



% Question 11
\newpage
\question[10] Being sure to simplify as much as possible, compute the following:
	\[
	\dfrac{9 - 5x}{x^2 + 7x - 8} - \dfrac{6x}{x - 1}
	\]



% Question 12
\newpage
\question[10] Being sure to simplify as much as possible, compute the following:
	\[
	\dfrac{x^2 + 4x - 5}{x^2 + 5x + 4} \cdot \dfrac{x^2 + 4x + 3}{x^2 + 3x - 10}
	\]



% Question 13
\newpage
\question[10] Being sure to simplify as much as possible, compute the following:
	\[
	\dfrac{\;\;\dfrac{x^2 - 9}{x^2 + 6x}\;\;}{\;\;\dfrac{x^2 + x - 6}{x^2 + 4x - 12}\;\;}
	\]



% Question 14
\newpage
\question[10] Find the domain of the function $f(x)= \dfrac{x^2 - 3x - 10}{x^2 - 4}$. Furthermore, identify any zeros, vertical asymptotes, horizontal asymptotes, and holes for the function $f(x)$. 



% Question 15
\newpage
\question[10] Explain why the function $f(x)= \dfrac{3x^2 + 4x - 8}{x + 3}$ has a slant asymptote. Find the slant asymptote for this function. 


\end{questions}
\end{document}