\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\setbool{quotetype}{false} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

\usepackage{actuarialsymbol}	% Actuary Symbols

% -------------------
% Content
% -------------------
\begin{document}

\homework{7: Due 02/14}{[David] The cedar planks out behind the motel, are they being used for something, or are they up for grabs? [Stevie] How do you know it's cedar? [David] Um, I bought a cologne once, in Japan, that's supposed to smell like the aftermath of a car crashing into a cedar tree.}{David Rose \& Stevie Budd, Schitt's Creek}

% Problem 1
\problem{10} Lue Zcar is going through a midlife crises and decides to buy a new luxury sports car. He asks his assistant to organize the loan. Lue's assistant organizes the loan, securing a \$354,750 loan at 6.42\% annual interest, compounded monthly over a period of 10~years. Mr. Zcar's payments will occur at the end of each month. 
	\begin{enumerate}[(a)]
	\item What are Lue's monthly payments?
	\item What is the total interest Lue will pay on this loan?
	\end{enumerate}



\newpage



% Problem 2
\problem{10} Sara Bellum is a neurobiologist looking to fund her lab. She approaches a local businessman, Faisal, for support. As he wants to support the sciences, he offers her very favorable terms: \$540,000 at 2.99\% annual interest, compounded semiannually for a period of 10~years. Determine to pay back the loan quickly, Sara will make equal, start of the month payments of \$5,194.33.
	\begin{enumerate}[(a)]
	\item How much does Sara still owe after 5~years of payments?
	\item At the end of 5~years, how much of Sara's payments actually go toward the loan? How much is paid in interest for this payment?
	\end{enumerate}


\end{document}