\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{homework}

% -------------------
% Content
% -------------------
\begin{document}
\homework{}

% Problem 1
\problem{10} There are 46~employees at a video game company. The company recently put out an immersive RPG. Of their employees, 14 worked on the story development and 13 worked on the programming, with 3 employees acting as intermediaries between the two groups by working on both. Selecting an employee at random from the company, what is the probability that\dots

\begin{enumerate}[(a)]
\item They worked on just the story?
\item They worked on the game at all?
\item They did not work on the game at all?
\item They worked on the story, assuming that they worked on the programming?
\item A story writer worked on the programming?
\end{enumerate}





\newpage





% Problem 2
\problem{10} A randomized algorithm uses two primary subroutines. The first subroutine is used 20\% of the time and gives a correct computation 59\% of the time, while it crashes 40\% of the time. The second subroutine gives the correct answer 50\% of the time. 

\begin{enumerate}[(a)]
\item Find the probability that the program uses the second subroutine to find the correct answer.
\item Find the probability that the program gives the correct answer.
\item Find the probability that the program crashes. 
\item Find the probability that the program uses the first subroutine, assuming it found the correct answer.
\item Find the probability that the program used the second subroutine, if the program crashed. 
\end{enumerate}





\newpage





% Problem 3
\problem{10} A weighted six-sided die has probabilities (partially) given below: \par
	\begin{table}[!ht]
	\centering
	\begin{tabular}{|c||c|c|c|c|c|c|} \hline
	$n$ & 1 & 2 & 3 & 4 & 5 & 6 \\ \hline
	$P(n)$ & $\dfrac{7}{10}$ & $\dfrac{1}{10}$ & $\dfrac{2}{10}$ & & $\dfrac{2}{10}$ & $\dfrac{1}{10}$ \\ \hline
	\end{tabular}
	\end{table} \par
Suppose a game is played using this die where if one rolls a 6, you win \$10, if you roll a 4 or 5 you win nothing, and if you roll a 2 or 3, you lose \$2, and if you roll a 2 you lose \$3. 

\begin{enumerate}[(a)]
\item Complete the probability table above.
\item Find the probability of rolling at least one 6 every 10~rolls. 
\item Find the expected value. Should one play this game? Explain.
\item What if one had to pay \$1 to play the game each time? How does this change the answer from (c)? 
\end{enumerate}






\newpage





% Problem 4
\problem{10} A ``$2^2$-face'' in a card game consists of having 2 face cards and 2 two's in one's five card hand. Being dealt five random cards from a standard 52 card deck, find the probability that one receives a ``$2^2$-face.'' 





\newpage





% Problem 5
\problem{10} Find the probability of getting a three of a kind in standard 5~card poker. \pspace


\end{document}