\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{10: Due 03/31}{We hang the petty thieves and appoint the great ones to public office.}{Aesop}

% Problem 1
\problem{10} Suppose you have a binomial distribution $B(11, 0.30)$. 
	\begin{enumerate}[(a)]
	\item Find the mean for this distribution. 
	\item Find the standard deviation for this distribution. 
	\item Find $P(X \geq 1)$. 
	\end{enumerate}



\newpage



% Problem 2
\problem{10} A recent study has shown that 33\% of Americans are struggling to meet their mortgage payments. To test the findings of this study, you take a random survey of 80 Americans with mortgages and determine how many of them are struggling to make their mortgage payments. Let $X$ denote the number of Americans in this survey that struggle meeting their mortgage and assume that the recent study has correct findings. Compute the following:
	\begin{enumerate}[(a)]
	\item The probability that at most 20 of them struggle making mortgage payments. 
	\item The probability that at least 20 of them struggle making mortgage payments. 
	\item The probability that at least 30 of them struggle making mortgage payments. 
	\item The probability that between 20 and 30 of them struggle making mortgage payments. 
	\end{enumerate}



\newpage



% Problem 3
\problem{10} In investigating political discourse in the nation, a research group does a study of people's satisfaction with political discourse. They are interested in determining the percentage of people that believe political discourse is becoming less productive. The survey they conduct estimates that 67\% of people (from a sample of 850 people) believe that political discourse is no longer productive. Assuming that this is a good estimate of the actual percentage, determine the following:
	\begin{enumerate}[(a)]
	\item The probability that at most 65\% of them believe political discourse is no longer productive. 
	\item The probability that at most 70\% of them believe political discourse is no longer productive. 
	\item The probability that between 65\% and 70\% of them believe political discourse is no longer productive. 
	\end{enumerate}


\end{document}