\documentclass[11pt,letterpaper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{../style/homework}
\usepackage{../style/commands}
\setbool{quotetype}{true} % True: Side; False: Under
\setbool{hideans}{true} % Student: True; Instructor: False

% -------------------
% Content
% -------------------
\begin{document}

\homework{6: Due 10/03}{If you fish can catch nothing, you have still caught a lesson.}{Matshona Dhliwayo}

% Problem 1
\problem{10} You are standing at the corner of 6th and 40th while your friend is standing at the corner of 2nd and 59th.
	\begin{enumerate}[(a)]
	\item How many blocks are you from your friend?
	\item How many blocks are you from your friend `as the crow flies'?
	\item What is your Euclidean distance between you and your friend?
	\item What is your Manhattan distance between you and your friend?
	\end{enumerate}



\newpage



% Problem 2
\problem{10} You see a plane at cruising altitude (approximately 38,000~ft) flying over a nearby airport. You know that the airport is 8.5~mi away. How far is the plane from you at this moment? [5,280~ft $=$ 1~mi]



\newpage



% Problem 3
\problem{10} Suppose you are designing a custom fish tank. The fish tank will be a rectangular box will be 36~in x 18~in x 19~in. The top will be open so that the tank can be accessed. 
	\begin{enumerate}[(a)]
	\item If you have to cover the exposed sides with a special plastic coating, what is the area of plastic coating that is needed per tank?
	\item How much water, in gallons, can the tank hold? [1~ft$^3 =$ 7.48052~gallon]
	\item Suppose you are going to put a volcano in the tank, which will have the shape of a right circular cone. If you put the largest possible volcano in the tank, how much water will it then take to fill the tank?
	\end{enumerate}



\newpage



% Problem 4
\problem{10} Suppose a courtyard at some hedge fund is approximately elliptical in shape. It is approximately 50~ft `the long way' and 35~ft `the short way.'
	\begin{enumerate}[(a)]
	\item What is the area of the courtyard?
	\item If someone can push mow approximately 320~square foot of lawn per minute, how long does it take to mow the courtyard?
	\item If every 1,000~square foot has to be fertilized with 10~lbs of fertilizer and the fertilizer costs \$2.08 per pound, how much does it cost to fertilize the courtyard?
	\end{enumerate}


\end{document}